---
title: "AAfMRI_trialwise_RSA"
author: "Jingyi"
date: "March/20/2024"
output: pdf_document
---

```{r setup, include=FALSE}
rm(list=ls(all=TRUE)) 
library(afex)
library(emmeans)
library(knitr)
library(tidyverse)
library(compute.es)
library(car)
library(ggplot2)
library(multcomp)
library(pastecs)
library(WRS2)
library(Hmisc)
library(tidyverse)
library(SuppDists)
library(ggpubr)
library(readxl)
library(ez)
library(nlme)
library(dplyr)
library(pacman)
p_load(reshape2, viridis, hrbrthemes,MASS,gridExtra,interactions)
knitr::opts_chunk$set(echo = TRUE)
`select` <- dplyr::select
`recode` <- dplyr::recode
options(contrasts=c("contr.sum","contr.poly"))
options(max.print = 10000)
```
```{r}
# Function to replace strings
transform_string <- function(s){
  s = gsub("harvardoxford_Hippocampus_bin60_2mm_Anterior", "aHPC", s)
  s = gsub("harvardoxford_Hippocampus_bin60_2mm_Mid", "midHPC", s)
  s = gsub("harvardoxford_Hippocampus_bin60_2mm_Posterior", "pHPC", s)
  s = gsub("harvardoxford_Hippocampus_bin60_2mm", "HPC", s)
  s = gsub("FS_entorhinal_exvivo.thresh", "Entorhinal", s)
  s = gsub("BA4_exvivo.thresh", "BA4", s)
  s = gsub("V1_exvivo.thresh", "V1", s)
  s = gsub("FS_", "", s)
  s = gsub("Amy_50_bin", "Amygdala", s)
  s = gsub("Amy_bin50_2mm", "Amygdala", s)
  s = gsub("AMY", "Amygdala", s)
  s = gsub("_2mm", "", s)
  s = gsub("lh.L_", "Left ", s)
  s = gsub("rh.R_", "Right ", s)  
    s = gsub("L_", "Left ", s)
  s = gsub("R_", "Right ", s)
  s = gsub("perirhinal_exvivo.thresh", "PRC", s)
  s = gsub("uni_", "", s)
  # s = gsub("_", " ", s)
  return (s)  
}
```

set group regression plot
```{r}
myGroupCorrelation_group_sub <- function(datainit, completevar, Formula1, Formula2, xvar, yvar, xlabel, ylabel, highcolor, modlinecolor, plottitle, fnamepdf, fnamepng, hjust){
  #Make sure all the rows contain values
  data <- datainit[complete.cases(datainit[[completevar]]), ]
  # Create predicted values based on the model
  tmp_ml <- lmer(Formula1, data = data, REML = FALSE)
tmp_summary <- summary(tmp_ml)
tmp_anova <- anova(tmp_ml)
p_value <- tmp_anova$`Pr(>F)`[1]

  if (round(as.numeric(p_value),3) >= 0.001){
    labelnow <- paste( " p = ", round(as.numeric(p_value), digits=3))
    
  }
else if (round(as.numeric(p_value), 3) < 0.001){
  labelnow <- "p < 0.001"
}

#just to trick the plot. But need to find a better solution
tmp_ml <- lmer(Formula2, data = data, REML = FALSE)
data$predictnum <- predict(tmp_ml,variances=list(fixef=TRUE,ranef=FALSE))

# Calculate the range for x and y
x_range <- range(data[[xvar]], na.rm = TRUE)
y_range <- range(data$predictnum, na.rm = TRUE)

# Calculate the y-values at the x limits of your data
intercept <- tmp_summary[["coefficients"]][1]
slope <- tmp_summary[["coefficients"]][2]

# Endpoints of the line
y_start <- slope * x_range[1] + intercept
y_end <- slope * x_range[2] + intercept

## Create a list of colors
# Extract participant list
pplst <- unique(data$sub)
nsub <- length(pplst)
# Define a list of colors from Blues (one per subject)
colour_lst2  <- scales::seq_gradient_pal(low = "#FCF5F2", high = highcolor, space = "Lab")(1:nsub/nsub)

# create values for scale colour manual (assign each color to a participant)
values_lst2 <- setNames(colour_lst2, pplst)

# create plot
pltnow <- ggplot(data,
                           aes(x = get(xvar),
                               y = predictnum,
                               color = factor(sub), group = factor(sub)))+
  geom_smooth(method = lm, se=F, size=0.3, alpha=0.5)+
  scale_color_manual(values = values_lst2)+
  # geom_abline(aes(intercept=`(Intercept)`, slope=get(xvar)), as.data.frame(t(fixef(tmp_ml))), lwd= 1,col = modlinecolor, size = 3) +
  geom_segment(aes(x = x_range[1], y = y_start, xend = x_range[2], yend = y_end), 
               lwd = 1, col = modlinecolor, size = 3) +
  # coord_cartesian(xlim = c(-2, 1)) +
  annotate("text", size= 4, x=Inf, y = Inf, label = labelnow,colour = "black",vjust=1.15, hjust=hjust)+
  ylab(ylabel)+
  xlab(xlabel)+
  theme_classic(base_size = 20) +
  labs(plottitle)+
  theme(axis.title.y = element_text(size = rel(1), angle = 90,  vjust=1.25))+
  theme(axis.title.x = element_text(size = rel(1), angle = 0,  vjust=0))+
  theme(axis.text.x = element_text(size=rel(1)))+
  theme(axis.text.y = element_text(size=rel(1)))+
  theme(legend.position="none")+
  theme(axis.line = element_line(colour = 'black', size = 0.5))+
  theme(axis.ticks = element_line(colour = "black", size = 0.5))+
      theme(axis.title.y = element_text(size = rel(0.85), angle = 90,  vjust=1.25))+
  theme(axis.title.x = element_text(size = rel(0.85), angle = 0,  vjust=0))+
  theme(axis.text.x = element_text(size=rel(0.85)))+
  theme(axis.text.y = element_text(size=rel(0.85)))
        # panel.grid.major = element_blank(),
        # panel.grid.minor = element_blank())

pltnow

ggsave(fnamepdf, width = 5.2, height = 4,dpi=300)
ggsave(fnamepng, width = 5.2, height = 4, dpi = 600)
}
```


Set color
```{r}
library("colorspace")
hcl_palettes(plot = TRUE)
BR<-diverging_hcl(5, palette = "Blue-Red 2")

colorList1 <- c(sequential_hcl(7, palette = "Mint"))
colorList2 <- c(sequential_hcl(7, palette = "Peach"))

colorList3 <- c(sequential_hcl(5, palette = "Reds"))
colorList4 <- c(sequential_hcl(5, palette = "Blues"))

list_2color <- c(colorList2[3], colorList1[3])
list_2color_1 <- c(colorList2[2], colorList1[2])

list_2color_2 <- c(colorList3[3], colorList4[2])

allcolor<-c(colorList2[5], colorList2[2], colorList1[5], colorList1[2])
allcolorEmoOrder<-c(colorList2[2],colorList1[5],colorList2[5],colorList1[2])
 
Failcolor <- BR[4]
"#E495A5"
Succcolor <- BR[2]
"#9DA8E2"
Betweencolor <- BR[3]

negcolor <- list_2color[1]
poscolor <- list_2color[2]

poscolor <- "#64A79A"
negcolor <- "#EF6D48"

regressline <- "#424242" #another option: "#7F7EBC"; "#86BFDE"
ribbonline <- "#BEBEBE"
"#7F7EBC"
"#86BFDE"
"#E1E1E1"
"#BEBEBE"
highcolor <- sequential_hcl(5, palette = "Grays")[3]
```
Merge dataframe from different masks and loop through masks
```{r}
# Set working directory to source file location
setwd("YOURRESULTSDIR/RSA/RSAbymask")
# Load the data
HPC <- read_csv("harvardoxford_Hippocampus_bin60_2mm_all_rsas_betas_whitened_trialwise_extended.csv")
#Remove sub 007 013, since bad motion
HPC <- HPC[!HPC$sub %in% c("007", "013","027", "081", "066", "057"),]


FPl <- read_csv("FS_FPl_all_rsas_betas_whitened_trialwise_extended.csv")
#Remove sub 007 013, since bad motion
FPl <- FPl[!FPl$sub %in% c("007", "013", "027", "081", "066", "057"),]
```

Merge
```{r}
myDataAll <- dplyr::bind_rows(HPC, FPl)
nrow(myDataAll)
length(unique(myDataAll$sub))
```


Add emotion change order column
```{r}
myDataAll$triallagnum <- myDataAll$triallag
myDataAll$triallagnum <- as.numeric(myDataAll$triallagnum)
myDataAll <- myDataAll %>% mutate(EmoOrder = case_when(triallagnum > 0 & StimVal1=="neg" & StimVal2 =="pos"~"neg2pos", triallagnum < 0 & StimVal1=="neg" & StimVal2 =="pos"~"pos2neg", triallagnum > 0 & StimVal1=="pos" & StimVal2 =="neg"~"pos2neg", triallagnum < 0 & StimVal1=="pos" & StimVal2 =="neg"~"neg2pos", StimVal1=="neg" & StimVal2 =="neg"~"neg2neg", StimVal1=="pos" & StimVal2 =="pos"~"pos2pos"))
myDataAll$EmoOrder <- as.factor(myDataAll$EmoOrder)
nrow(myDataAll)

myDataAll <- myDataAll %>% mutate(firstval = case_when(EmoOrder=="pos2pos"|EmoOrder=="pos2neg" ~ "Positive", EmoOrder=="neg2pos"|EmoOrder=="neg2neg" ~ "Negative"))
myDataAll$firstval <- as.factor(myDataAll$firstval)

myDataAll <- myDataAll %>% mutate(secondval = case_when(EmoOrder=="pos2pos"|EmoOrder=="neg2pos" ~ "Positive", EmoOrder=="pos2neg"|EmoOrder=="neg2neg" ~ "Negative"))
myDataAll$secondval <- as.factor(myDataAll$secondval)

myDataAll <- myDataAll %>% mutate(PerciseBiasSign1 = case_when(Tprecise_bias1> 0 ~ 1, Tprecise_bias1 < 0 ~ -1))
myDataAll$PerciseBiasSign1 <- as.factor(myDataAll$PerciseBiasSign1)
levels(myDataAll$PerciseBiasSign1) <- c("End", "Beginning")

myDataAll <- myDataAll %>% mutate(PerciseBiasSign2 = case_when(Tprecise_bias2> 0 ~ 1, Tprecise_bias2 < 0 ~ -1))
myDataAll$PerciseBiasSign2 <- as.factor(myDataAll$PerciseBiasSign2)
levels(myDataAll$PerciseBiasSign2) <- c("End", "Beginning")

myDataAll <- myDataAll %>% dplyr::mutate(triallagsign = case_when(triallagnum > 0 ~ 1, triallagnum < 0 ~ -1))
myDataAll$triallagsign <- as.factor(myDataAll$triallagsign)
```

**reverse the Tprecise_bias so that Estimates - Actual position**
Larger bias -> towards End
Smaller bias -> towards beginning
```{r}
myDataAll$Tprecise_bias1 <- (-1) * myDataAll$Tprecise_bias1
myDataAll$Tprecise_bias2 <- (-1) * myDataAll$Tprecise_bias2
```

Set factors
```{r}
myDataAll$aromn1 <- as.numeric(myDataAll$aromn1)
myDataAll$valmn1 <- as.numeric(myDataAll$valmn1)
myDataAll$EmoChange <- as.factor(myDataAll$EmoChange)
myDataAll$StimVal1 <- as.factor(myDataAll$StimVal1)
myDataAll$PerciseBiasFlag1 <- as.factor(myDataAll$PerciseBiasFlag1)
myDataAll$PercisepChanceFlag1 <- as.factor(myDataAll$PercisepChanceFlag1)
myDataAll$RunBias1Flag1 <- as.factor (myDataAll$RunBias1Flag1)
myDataAll$RunBias2Flag1 <- as.factor(myDataAll$RunBias2Flag1)
myDataAll$Tprecise_bias1 <- as.numeric(myDataAll$Tprecise_bias1)
myDataAll$trial1 <- as.factor(myDataAll$trial1)
myDataAll$Trun_bias1<-as.numeric(myDataAll$Trun_bias1)
myDataAll$Trun_biasabs1<-as.numeric(myDataAll$Trun_biasabs1)
myDataAll$sub <- as.numeric(as.character(myDataAll$sub))
myDataAll$triallag <- as.factor(myDataAll$triallag)
myDataAll$DistanceIndex <- as.numeric(myDataAll$DistanceIndex)
myDataAll$corr <- as.numeric(myDataAll$corr)
myDataAll$corr_z <- as.numeric(myDataAll$corr_z)
myDataAll$ReconMem1 <- as.factor(myDataAll$ReconMem1)
levels(myDataAll$ReconMem1) <- c("Recognized", "Forgotten")
myDataAll$ReconMem2 <- as.factor(myDataAll$ReconMem2)
levels(myDataAll$ReconMem2) <- c("Recognized", "Forgotten")
myDataAll$ConfReconMem1 <- as.numeric(myDataAll$ConfReconMem1)
myDataAll$ConfReconMem2 <- as.numeric(myDataAll$ConfReconMem2)
```

add actiongoal column
```{r}
myDataAll <- myDataAll %>% mutate(ActionGoal = case_when(condition1 == "neg_app" ~ "Apporach", condition1 == "pos_app" ~ "Apporach", condition1 == "neg_avoid" ~ "Avoid", condition1 == "pos_avoid" ~ "Avoid"))
myDataAll$ActionGoal <- as.factor(myDataAll$ActionGoal)

myDataAll <- myDataAll %>% mutate(ActionGoal1 = case_when(condition1 == "neg_app" ~ "Apporach", condition1 == "pos_app" ~ "Apporach", condition1 == "neg_avoid" ~ "Avoid", condition1 == "pos_avoid" ~ "Avoid"))
myDataAll$ActionGoal1 <- as.factor(myDataAll$ActionGoal1)

myDataAll <- myDataAll %>% mutate(ActionGoal2 = case_when(condition2 == "neg_app" ~ "Apporach", condition2 == "pos_app" ~ "Apporach", condition2 == "neg_avoid" ~ "Avoid", condition2 == "pos_avoid" ~ "Avoid"))
myDataAll$ActionGoal2 <- as.factor(myDataAll$ActionGoal2)

myDataAll <- myDataAll %>% mutate(ActionChange = case_when(ActionGoal1=="Apporach"&ActionGoal2=="Apporach" ~ "non-change", ActionGoal1=="Avoid"&ActionGoal2=="Avoid" ~ "non-change", ActionGoal1=="Apporach"&ActionGoal2=="Avoid" ~ "change", ActionGoal1=="Avoid"&ActionGoal2=="Apporach" ~ "change"))
myDataAll$ActionChange <- as.factor(myDataAll$ActionChange)
```

add absolute LAG column
```{r}
myDataAll$triallagabs <- abs(myDataAll$triallagnum)
myDataAll$triallagabs <- as.factor(myDataAll$triallagabs)
```

##Load univariate betas with pre-whitten values
```{r}
AMY_whitten <- read.csv("YOURRESULTSDIR/AA_fMRIAnalyses/fMRIAnalysis/AMY_uni/Amy_50_bin_univariate.csv")
AMY_whitten <- AMY_whitten[AMY_whitten$mask=="Amy_50_bin",]
nrow(AMY_whitten)
```
Merge
```{r}
colnames(AMY_whitten) <- c("sub", "mask", "run", "trial1", "ImgStim1", "value_AMY", "uni_whiten_AMY")
AMY_whitten <- AMY_whitten %>% select("sub", "run", "trial1", "ImgStim1", "uni_whiten_AMY")
AMY_whitten$trial1 <- as.factor(AMY_whitten$trial1)
myDataAll <- dplyr::left_join(myDataAll, AMY_whitten, by = c("sub", "run", "trial1", "ImgStim1"))
nrow(myDataAll)
```

##Add the ImgSim column
```{r}
#load the image similarity matrix
ImgSim <- read.csv("YOURRESULTSDIR/SemanticSimilarityStim/image_pair/corr_mat/ImageSimilarity.csv", header = TRUE)
```
reshape the matrix
```{r}
# 1. Make imgID the rownames and remove it from columns
rownames(ImgSim) <- ImgSim$imgID
ImgSim$imgID <- NULL

# 2. Rename the column names to match the rownames (symmetric matrix)
colnames(ImgSim) <- rownames(ImgSim)

# 3. Melt the matrix to long format (full matrix)
ImgSim_long <- reshape2::melt(as.matrix(ImgSim), varnames = c("ImgStim1", "ImgStim2"), value.name = "value")
```

Add the ImgSemantic column
```{r}
myDataAll <- myDataAll %>%
  rowwise() %>%
 mutate(
    stimA = min(ImgStim1, ImgStim2),
    stimB = max(ImgStim1, ImgStim2)
  ) %>%
  ungroup() %>%
  dplyr::left_join(ImgSim_long, by = c("ImgStim1" = "ImgStim1", "ImgStim2" = "ImgStim2")) 
# %>%
myDataAll <- myDataAll %>% dplyr::rename(ImgSemantic = value)
myDataAll$ImgSemantic <- as.numeric(myDataAll$ImgSemantic)
```
```{r}
myDataAll$residTprecise1 <- as.numeric(myDataAll$residTprecise1)
myDataAll$residTprecise2 <- as.numeric(myDataAll$residTprecise2)

myDataAll$residTpreciseabs1 <- as.numeric(myDataAll$residTpreciseabs1)
myDataAll$residTpreciseabs2 <- as.numeric(myDataAll$residTpreciseabs2)

myDataAll$PreciseBiaslmFlag1 <- as.factor(myDataAll$PreciseBiaslmFlag1)
myDataAll$PreciseBiaslmFlag2 <- as.factor(myDataAll$PreciseBiaslmFlag2)
```

**Add Temporal Memory filter column**
```{r}
TempMemppBad <- c(5, 6, 11, 13, 30, 36, 38, 53, 54, 64)

myDataAll <- myDataAll %>%
  mutate(
    TempMemfilter = if_else(sub %in% TempMemppBad, 0, 1)
  )

myDataAll_memfiltered <- myDataAll[myDataAll$TempMemfilter != 0,]
length(unique(myDataAll_memfiltered$sub))
```


##Relationship of between-trial pattern correlation and temporal memory accuracy
Correlation for precise bias
```{r}
BiasBeta <- c()
BiasSE <- c()
BiasF <- c()
Biasp <- c()

triallagBeta <- c()
triallagSE <- c()
triallagF <- c()
triallagp <- c()

BiasLagInterBeta <- c()
BiasLagInterSE <- c()
BiasLagInterF <- c()
BiasLagInterp <- c()

masklist <- c()

maskli <- c("FS_FPl", "harvardoxford_Hippocampus_bin60_2mm")

for (ThisMask in maskli){
  masklist <- append(masklist, ThisMask)
  # ThisMask <- "FS_FPl"
  myData_subset= myDataAll_memfiltered[myDataAll_memfiltered$mask==ThisMask & myDataAll_memfiltered$PerciseBiasFlag1 %in% c("MemFail", "MemSuccess") & myDataAll_memfiltered$triallag %in% c(-4, -3, -2, -1, 1, 2, 3, 4),] 
  mod <- lmer(corr_z~PerciseBiasFlag1*triallag + valmn1 + aromn1 + ActionGoal +EmoChange+ ActionChange+ order + ImgSemantic + (valmn1 + ActionGoal|sub), control = lmerControl(optimizer = "bobyqa"), data=myData_subset, REML =FALSE)
  summod <- summary(mod)
  betanow <- summod[["coefficients"]][2,1]
  aovmod <-anova(mod)
  pnow <- round(aovmod$`Pr(>F)`[1], 3)
  
BiasBeta <- append(BiasBeta, summod[["coefficients"]][2,1])
BiasSE <- c(BiasSE, summod[["coefficients"]][2,2])
BiasF <- c(BiasF, aovmod$`F value`[1])
Biasp <- c(Biasp, aovmod$`Pr(>F)`[1])

triallagBeta <- append(triallagBeta, summod[["coefficients"]][3,1])
triallagSE <- c(triallagSE, summod[["coefficients"]][3,2])
triallagF <- c(triallagF, aovmod$`F value`[2])
triallagp <- c(triallagp, aovmod$`Pr(>F)`[2])

BiasLagInterBeta <- c(BiasLagInterBeta, summod[["coefficients"]][16,1])
BiasLagInterSE <- c(BiasLagInterSE, summod[["coefficients"]][16,2] )
BiasLagInterF <- c(BiasLagInterF, aovmod$`F value`[10])
BiasLagInterp <- c(BiasLagInterp, aovmod$`Pr(>F)`[10])
  
  if (pnow > 0.001){
  text_label <- paste0("p = ", pnow)
  }
  else{
    text_label <- "p < 0.001"
  }
if (ThisMask == "harvardoxford_Hippocampus_bin60_2mm"){
  colorvalue = c("#8FBFD8", "#077EAD")
}
else if (ThisMask == "FS_FPl"){
  colorvalue = c("#B89BB2", "#AD4993")
}
else{colorvalue = c("#BEBEBE", "#424242")}
  
  ylabel=sprintf("%s Pattern Correlation (z)", transform_string(ThisMask))
  fnamepdf=sprintf("/Users/jingyiwang/Dropbox/LEAP_Neuro_Lab/researchProjects/jingyi_documents/emotion_motor_grant/Manuscripts/MemoryMS/Figures/RawPlots/%s_lagMem_corr_Memfilter.pdf", ThisMask)
  fnamepng=sprintf("/Users/jingyiwang/Dropbox/LEAP_Neuro_Lab/researchProjects/jingyi_documents/emotion_motor_grant/Manuscripts/MemoryMS/Figures/RawPlots/%s_lagMem_corr_Memfilter.png", ThisMask)
  library(dplyr)
myData_subset_grouped <- myData_subset %>% group_by(sub, triallag, PerciseBiasFlag1)%>%dplyr::summarize(corr_z=mean(corr_z, na.rm=TRUE))
detach("package:dplyr", force=TRUE)
myData_subset_grouped_sum <- summarySEwithin(myData_subset_grouped, measurevar="corr_z", idvar=c("sub"),withinvars=c("PerciseBiasFlag1", "triallag"), na.rm=TRUE, conf.interval=.95)
library(dplyr)
ymax <- max(myData_subset_grouped_sum$corr_z) + max(myData_subset_grouped_sum$se)
  #plot lines and save
# Line plot with multiple groups
ggplot(data=myData_subset_grouped_sum, aes(x=triallag, y=corr_z, group=PerciseBiasFlag1)) +
  geom_errorbar(aes(ymin=corr_z-se, ymax=corr_z+se), width=.2) +
  geom_line(aes(color=PerciseBiasFlag1), size=0.6)+
  # geom_line(size=1.5)+
  geom_point(aes(color=PerciseBiasFlag1), size=0.6)+
# labs(title=ThisMask)+
  ylab(ylabel)+
  xlab("LAG")+
  theme(legend.position = "right")+
  annotate(
      "text", x = Inf, y = ymax+0.005, label = text_label, 
      hjust = 1, vjust = 1, size = 3, color = "black") +
  scale_color_manual(values=colorvalue, name = "Temporal Memory",labels = c("Low", "High"))+
theme_classic(base_size = 20) +
  theme(axis.title.y = element_text(size = rel(1), angle = 90,  vjust=1.25))+
  theme(axis.title.x = element_text(size = rel(1), angle = 0,  vjust=0))+
  theme(axis.text.x = element_text(size=rel(1)))+
  theme(axis.text.y = element_text(size=rel(1)))+
  # theme(legend.position="none")+
  theme(axis.line = element_line(colour = 'black', size = 0.5))+
  theme(axis.ticks = element_line(colour = "black", size = 0.5))+
      theme(axis.title.y = element_text(size = rel(0.85), angle = 90,  vjust=1.25))+
  theme(axis.title.x = element_text(size = rel(0.85), angle = 0,  vjust=0))+
  theme(axis.text.x = element_text(size=rel(0.85)))+
  theme(axis.text.y = element_text(size=rel(0.85)))
        # panel.grid.major = element_blank(),
        # panel.grid.minor = element_blank())
 ggsave(fnamepdf,height=4, width=8, dpi=300)
  ggsave(fnamepng,height=4, width=8, dpi=300)
}

sumdflag <- data.frame(masklist, BiasBeta, BiasSE, BiasF, Biasp, triallagBeta, triallagSE, triallagF, triallagp, BiasLagInterBeta, BiasLagInterSE, BiasLagInterF, BiasLagInterp)
sumdflag$Biasp <- round(sumdflag$Biasp, 3)
```
##FPl
```{r}
ThisMask <- "FS_FPl"
  myData_subset= myDataAll_memfiltered[myDataAll_memfiltered$mask==ThisMask & myDataAll_memfiltered$PerciseBiasFlag1 %in% c("MemFail", "MemSuccess") & myDataAll_memfiltered$triallag %in% c(-4, -3, -2, -1, 1, 2, 3, 4),] 
  mod <- lmer(corr_z~PerciseBiasFlag1*triallag + valmn1 + aromn1 + ActionGoal +EmoChange+ ActionChange+ order + ImgSemantic + (valmn1 + ActionGoal|sub), control = lmerControl(optimizer = "bobyqa"), data=myData_subset, REML =FALSE)
  summod <- summary(mod)
  summod
  betanow <- summod[["coefficients"]][2,1]
  aovmod <-anova(mod)
  pnow <- round(aovmod$`Pr(>F)`[1], 3)
```

```{r}
ThisMask <- "FS_FPl"
  myData_subset= myDataAll_memfiltered[myDataAll_memfiltered$mask==ThisMask & myDataAll_memfiltered$PerciseBiasFlag1 %in% c("MemFail", "MemSuccess") & myDataAll_memfiltered$triallag %in% c(-4, -3, -2, -1, 1, 2, 3, 4),] 
  mod <- lmer(corr_z~PerciseBiasFlag1*triallag + valmn1 + aromn1 + ActionGoal +EmoChange+ ActionChange+ order + ImgSemantic + ReconMem1 + (valmn1 + ActionGoal|sub), control = lmerControl(optimizer = "bobyqa"), data=myData_subset, REML =FALSE)
  summod <- summary(mod)
  summod
  betanow <- summod[["coefficients"]][2,1]
  aovmod <-anova(mod)
  pnow <- round(aovmod$`Pr(>F)`[1], 3)
```

##HPC
```{r}
ThisMask <- "harvardoxford_Hippocampus_bin60_2mm"
  myData_subset= myDataAll_memfiltered[myDataAll_memfiltered$mask==ThisMask & myDataAll_memfiltered$PerciseBiasFlag1 %in% c("MemFail", "MemSuccess") & myDataAll_memfiltered$triallag %in% c(-4, -3, -2, -1, 1, 2, 3, 4),] 
  mod <- lmer(corr_z~PerciseBiasFlag1*triallag + valmn1 + aromn1 + ActionGoal +EmoChange+ ActionChange+ order + ImgSemantic + (valmn1 + ActionGoal|sub), control = lmerControl(optimizer = "bobyqa"), data=myData_subset, REML =FALSE)
  summod <- summary(mod)
  summod
  betanow <- summod[["coefficients"]][2,1]
  aovmod <-anova(mod)
  pnow <- round(aovmod$`Pr(>F)`[1], 3)
```

```{r}
ThisMask <- "harvardoxford_Hippocampus_bin60_2mm"
  myData_subset= myDataAll_memfiltered[myDataAll_memfiltered$mask==ThisMask & myDataAll_memfiltered$PerciseBiasFlag1 %in% c("MemFail", "MemSuccess") & myDataAll_memfiltered$triallag %in% c(-4, -3, -2, -1, 1, 2, 3, 4),] 
  mod <- lmer(corr_z~PerciseBiasFlag1*triallag + valmn1 + aromn1 + ActionGoal +EmoChange+ ActionChange+ order + ImgSemantic + ReconMem1 + (valmn1 + ActionGoal|sub), control = lmerControl(optimizer = "bobyqa"), data=myData_subset, REML =FALSE)
  summod <- summary(mod)
  summod
  betanow <- summod[["coefficients"]][2,1]
  aovmod <-anova(mod)
  pnow <- round(aovmod$`Pr(>F)`[1], 3)
```

##Relationship between between-trial pattern correlation and amygdala activation
For loop for different brain areas and lags
```{r}
maskli <- c("FS_FPl", "harvardoxford_Hippocampus_bin60_2mm")

uniAMYBeta <- c()
uniAMY_p <- c()

valmnBeta <- c()
valmn_p <- c()

aromnBeta <- c()
aromn_p <- c()

Maskli <- c()
Lag <- c()
for (tmpMask in maskli){
  for (tmptriallag in c(1, -1)){
    #tmptriallag <- 1
    #tmpMask <- "FPl"
    tmpdf <- myDataAll[myDataAll$mask==tmpMask & myDataAll$triallag==tmptriallag,]
    
    tmpmod <- lmer(corr_z~uni_whiten_AMY + valmn1 + aromn1 +ActionGoal+EmoChange+ActionChange+ImgSemantic+(valmn1+ActionGoal|sub), data=tmpdf, REML =FALSE, control = lmerControl(optimizer = "bobyqa"))
    summod <- summary(tmpmod)
    aovmod <- anova(tmpmod)
    
    uniAMYBeta <- append(uniAMYBeta, round(summod[["coefficients"]][2, 1], 3))
    uniAMY_p <- append(uniAMY_p, round(aovmod$`Pr(>F)`[1], 3))
    
    valmnBeta <- append(valmnBeta, round(summod[["coefficients"]][3, 1], 3))
    valmn_p <- append(valmn_p, round(aovmod$`Pr(>F)`[2], 3))
    
    aromnBeta <- append(aromnBeta, round(summod[["coefficients"]][4, 1], 3))
    aromn_p <- append(aromn_p, round(aovmod$`Pr(>F)`[3], 3))
    
    Maskli <- append(Maskli, tmpMask)
    Lag <- append(Lag, tmptriallag)

    fnamepdf<-sprintf("/Users/jingyiwang/Dropbox/LEAP_Neuro_Lab/researchProjects/jingyi_documents/emotion_motor_grant/Manuscripts/MemoryMS/Figures/RawPlots/AmyUniwhitten_PS_lag%s_%s_memfilter.pdf", tmptriallag, tmpMask)
fnamepng<-sprintf("/Users/jingyiwang/Dropbox/LEAP_Neuro_Lab/researchProjects/jingyi_documents/emotion_motor_grant/Manuscripts/MemoryMS/Figures/RawPlots/AmyUniwhitten_PS_lag%s_%s_memfilter.png", tmptriallag, tmpMask)
# "#2859BB"
# '#1627BB'

xlabel<-"Amygdala Activation"
ylabel<-sprintf("%s Pattern Correlation (z)", transform_string(tmpMask))
plotTitle <- ""

if (tmpMask=="FS_FPl"){
  #regressline <- "#9CD2A1" #for MDRS
  regressline <- "#B64097"
  
  
}
else if (tmpMask=="Amy_50_bin"){
  regressline <- "#EAA48F"
}
else{
  regressline <- "#95BBD8"
}

# myGroupCorrelation_group(tmpdf, "uni_AMY","corr_z", xlabel, ylabel,"#2859BB", '#1627BB', plotTitle, fnamepdf, fnamepng)
myGroupCorrelation_group_sub(tmpdf, "uni_whiten_AMY", "corr_z~uni_whiten_AMY + valmn1 + aromn1 +ActionGoal+EmoChange+ActionChange+ImgSemantic+(valmn1+ActionGoal|sub)", "corr_z~uni_whiten_AMY + valmn1 + aromn1 +ActionGoal+EmoChange+ActionChange+ImgSemantic+(valmn1+ActionGoal|sub)", "uni_whiten_AMY", "corr_z", xlabel, ylabel, highcolor, regressline, plotTitle, fnamepdf, fnamepng, 1)
  }
}
sumuniAMYPSWhitten_memfilter <- data.frame(Maskli, Lag, uniAMYBeta, uniAMY_p, valmnBeta, valmn_p, aromnBeta, aromn_p)
```

###FPl
```{r}
tmptriallag <- 1
tmpMask <- "FS_FPl"
    tmpdf <- myDataAll[myDataAll$mask==tmpMask & myDataAll$triallag==tmptriallag,]
    
    tmpmod <- lmer(corr_z~uni_whiten_AMY + valmn1 + aromn1 +ActionGoal+EmoChange+ActionChange+ImgSemantic+(valmn1+ActionGoal|sub), data=tmpdf, REML =FALSE, control = lmerControl(optimizer = "bobyqa"))
    summod <- summary(tmpmod)
    summod
    aovmod <- anova(tmpmod)
    aovmod
```

```{r}
tmptriallag <- 1
tmpMask <- "FS_FPl"
    tmpdf <- myDataAll[myDataAll$mask==tmpMask & myDataAll$triallag==tmptriallag,]
    
    tmpmod <- lmer(corr_z~uni_whiten_AMY + valmn1 + aromn1 +ActionGoal+EmoChange+ActionChange+ImgSemantic+ReconMem1+(valmn1+ActionGoal|sub), data=tmpdf, REML =FALSE, control = lmerControl(optimizer = "bobyqa"))
    summod <- summary(tmpmod)
    summod
    aovmod <- anova(tmpmod)
    aovmod
```
###HPC
```{r}
tmptriallag <- 1
tmpMask <- "harvardoxford_Hippocampus_bin60_2mm"
    tmpdf <- myDataAll[myDataAll$mask==tmpMask & myDataAll$triallag==tmptriallag,]
    
    tmpmod <- lmer(corr_z~uni_whiten_AMY + valmn1 + aromn1 +ActionGoal+EmoChange+ActionChange+ImgSemantic+(valmn1+ActionGoal|sub), data=tmpdf, REML =FALSE, control = lmerControl(optimizer = "bobyqa"))
    summod <- summary(tmpmod)
    summod
    aovmod <- anova(tmpmod)
    aovmod
```
```{r}
tmptriallag <- 1
tmpMask <- "harvardoxford_Hippocampus_bin60_2mm"
    tmpdf <- myDataAll[myDataAll$mask==tmpMask & myDataAll$triallag==tmptriallag,]
    
    tmpmod <- lmer(corr_z~uni_whiten_AMY + valmn1 + aromn1 +ActionGoal+EmoChange+ActionChange+ImgSemantic+ReconMem1+(valmn1+ActionGoal|sub), data=tmpdf, REML =FALSE, control = lmerControl(optimizer = "bobyqa"))
    summod <- summary(tmpmod)
    summod
    aovmod <- anova(tmpmod)
    aovmod
```








