---
title: "AAfMRI_CoarseMem"
author: "Jingyi"
date: "Aug/1/2022"
output: pdf_document
---

```{r setup, include=FALSE}
rm(list=ls(all=TRUE)) 
library(afex)
library(emmeans)
library(knitr)
library(tidyverse)
library(compute.es)
library(car)
library(ggplot2)
library(multcomp)
library(pastecs)
library(WRS2)
library(Hmisc)
library(tidyverse)
library(SuppDists)
library(ggpubr)
library(readxl)
library(ez)
library(nlme)
library(dplyr)
library(pacman)
p_load(reshape2, viridis, hrbrthemes,MASS,gridExtra)
knitr::opts_chunk$set(echo = TRUE)
`select` <- dplyr::select
`recode` <- dplyr::recode
options(contrasts=c("contr.sum","contr.poly"))
```
Get data
```{r}
# Set working directory to source file location
setwd("YOURRESULTSDIR")
# Load the data
CoarseMemData <- read_csv("CoarseMem_sorted.csv")

```
```{r}
myScatterPlotSFN <- function (data, fname, xvar, yvar, xlabel,ylabel, color, plotTitle, pvalue, rvalue) {
  if(NROW(data)>3){
     if (pvalue > 0.001 & pvalue <= 0.005){
      annotationNow <- paste0("r = ", round(rvalue, digits=2)," ", "**")
    }
    else if (pvalue <= 0.001){
      annotationNow <- paste0("r = ", round(rvalue, digits=2)," ", "***")
    }
    else if (pvalue > 0.005 & pvalue <= 0.05){
      annotationNow <- paste0("r = ", round(rvalue, digits=2), " ","*")
    }
    else if (pvalue > 0.05){
      annotationNow <- paste0("r = ", round(rvalue, digits=2))
    }
    # rhovalue=with(data, cor.test(get(xvar),get(yvar), use = "complete.obs", method="spearman",exact=FALSE ))
    ggplot(data, aes_string(x=xvar, y=yvar)) +
      geom_point(shape = 21, colour = "black", fill = color, size = 1, stroke = 0.5, alpha=1/10)+
      # geom_point(shape=19,  size = 3, colour=color, alpha = 1/10) + 
      geom_smooth(method=lm, colour=color, size = 1.25, fill = color, se=TRUE ) + # Add linear regression lines #999999
      theme_classic(base_size=20)+ #gray or bw # original 15
      # scale_y_continuous(expand = c(0,0),limits = c(0,ymax))+ #Set the y-axis limits
      # ylim = ymax +
      xlab(xlabel) + 
      ylab(ylabel) +  
      ggtitle(plotTitle)+
      annotate("text", size= 2, x=Inf, y = Inf, label = annotationNow,colour = "black",vjust=1.1, hjust=1)   +
     # annotate("text", size= 2, x=Inf, y = Inf, label = annotationNow,colour = "black",vjust=20, hjust=1)   + #20
      theme(axis.line = element_line(colour = 'black', size = 0.5))+
  theme(axis.ticks = element_line(colour = "black", size = 0.25))+
      theme(plot.title = element_text(hjust = 0.5), panel.grid.major=element_blank(),panel.grid.minor=element_blank(),panel.background=element_blank())+
      scale_y_continuous(limits = c(0,100))
    ggsave(fname,height=4, width=4.5, dpi=300)
  }}
```
set group regression plot
```{r}
myGroupCorrelation_group_sub <- function(datainit, completevar, Formula,  xvar, yvar, xlabel, ylabel, highcolor, modlinecolor, plottitle, fnamepdf, fnamepng, hjust){
  #Make sure all the rows contain values
  data <- datainit[complete.cases(datainit[[completevar]]), ]
  data$sub <- data$participant
  # Create predicted values based on the model
  tmp_ml <- lmer(Formula, data = data, REML =FALSE)
tmp_summary <- summary(tmp_ml)
tmp_anova <- anova(tmp_ml)
p_value <- tmp_anova$`Pr(>F)`[1]

  if (round(as.numeric(p_value),3) >= 0.001){
    labelnow <- paste( " p = ", round(as.numeric(p_value), digits=3))
    
  }
else if (round(as.numeric(p_value), 3) < 0.001){
  labelnow <- "p < 0.001"
}

#just to trick the plot. But need to find a better solution
tmp_ml <- lmer(Formula, data = data, REML = FALSE)
data$predictnum <- predict(tmp_ml,variances=list(fixef=TRUE,ranef=FALSE))

# Calculate the range for x and y
x_range <- range(data[[xvar]], na.rm = TRUE)
y_range <- range(data$predictnum, na.rm = TRUE)

# Calculate the y-values at the x limits of your data
intercept <- tmp_summary[["coefficients"]][1]
slope <- tmp_summary[["coefficients"]][2]

# Endpoints of the line
y_start <- slope * x_range[1] + intercept
y_end <- slope * x_range[2] + intercept

## Create a list of colors
# Extract participant list
pplst <- unique(data$sub)
nsub <- length(pplst)
# Define a list of colors from Blues (one per subject)
colour_lst2  <- scales::seq_gradient_pal(low = "#FCF5F2", high = highcolor, space = "Lab")(1:nsub/nsub)

# create values for scale colour manual (assign each color to a participant)
values_lst2 <- setNames(colour_lst2, pplst)

# create plot
pltnow <- ggplot(data,
                           aes(x = get(xvar),
                               y = predictnum,
                               color = factor(sub), group = factor(sub)))+
  geom_smooth(method = lm, se=F, size=0.3, alpha=0.5)+
  scale_color_manual(values = values_lst2)+
  # geom_abline(aes(intercept=`(Intercept)`, slope=get(xvar)), as.data.frame(t(fixef(tmp_ml))), lwd= 1,col = modlinecolor, size = 3) +
  geom_segment(aes(x = x_range[1], y = y_start, xend = x_range[2], yend = y_end), 
               lwd = 1, col = modlinecolor, size = 3) +
  # coord_cartesian(xlim = c(-2, 1)) +
  annotate("text", size= 4, x=Inf, y = Inf, label = labelnow,colour = "black",vjust=1.15, hjust=hjust)+
  ylab(ylabel)+
  xlab(xlabel)+
  theme_classic(base_size = 20) +
  
  theme(axis.title.y = element_text(size = rel(1), angle = 90,  vjust=1.25))+
  theme(axis.title.x = element_text(size = rel(1), angle = 0,  vjust=0))+
  theme(axis.text.x = element_text(size=rel(1)))+
  theme(axis.text.y = element_text(size=rel(1)))+
  theme(legend.position="none")+
  theme(axis.line = element_line(colour = 'black', size = 0.5))+
  theme(axis.ticks = element_line(colour = "black", size = 0.5))+
      theme(axis.title.y = element_text(size = rel(0.85), angle = 90,  vjust=1.25))+
  theme(axis.title.x = element_text(size = rel(0.85), angle = 0,  vjust=0))+
  theme(axis.text.x = element_text(size=rel(0.85)))+
  theme(axis.text.y = element_text(size=rel(0.85)))+
  scale_y_continuous(labels = scales::number_format(accuracy = 0.1,))+
  labs(title = plottitle)
        # panel.grid.major = element_blank(),
        # panel.grid.minor = element_blank())

pltnow

ggsave(fnamepdf, width = 4.5, height = 4,dpi=300)
ggsave(fnamepng, width = 4.5, height = 4, dpi = 600)
}
```

Set color
```{r}
library("colorspace")
# hcl_palettes(plot = TRUE)
BR<-diverging_hcl(5, palette = "Blue-Red 2")
allcolor<-c(BR[1], BR[5], BR[2], BR[4])

colorList1 <- c(sequential_hcl(7, palette = "Mint"))
colorList2 <- c(sequential_hcl(7, palette = "Peach"))

colorList3 <- c(sequential_hcl(5, palette = "Reds"))
colorList4 <- c(sequential_hcl(5, palette = "Blues"))

list_2color <- c(colorList2[3], colorList1[3])
list_2color_1 <- c(colorList2[2], colorList1[2])

list_2color_2 <- c(colorList3[3], colorList4[2])
 
# Failcolor <- allcolor[5]
# Succcolor <- allcolor[1]

negcolor <- list_2color[1]
poscolor <- list_2color[2]

Failcolor <- list_2color_2[1]
Succcolor <- list_2color_2[2]

regressline <- "#424242" #another option: "#7F7EBC"; "#86BFDE"
ribbonline <- "#BEBEBE"
"#7F7EBC"
"#86BFDE"
"#E1E1E1"
"#BEBEBE"
highcolor <- sequential_hcl(5, palette = "Grays")[3]
```


**calculate the precise bias and coarse bias**
The precise bias absolute = |precise time points - estimated time point|
The precise bias = precise time points - estimated time point
The coarse bias absolute = |run - estimated run|
The coarse bias  = run - estimated run #positive estimated the onset earlier than real onset, negative estimated the onset later than real onset.
##Get variables ready
scale real time to slider metrics
```{r}
CoarseMemData$Treal_precise=(8/CoarseMemData$TotalTime)*(CoarseMemData$image.started-CoarseMemData$Start)
CoarseMemData$Testimate_precise=CoarseMemData$CoarseTemp_slider.response
CoarseMemData$Tprecise_biasabs=abs(CoarseMemData$Treal_precise-CoarseMemData$Testimate_precise)
CoarseMemData$Tprecise_bias=CoarseMemData$Treal_precise-CoarseMemData$Testimate_precise
CoarseMemData$Testimate_run=ceiling(CoarseMemData$CoarseTemp_slider.response)
CoarseMemData$Trun_biasabs=abs(CoarseMemData$run-CoarseMemData$Testimate_run)
CoarseMemData$Trun_bias=CoarseMemData$run-CoarseMemData$Testimate_run
```

Change type of the variables.
```{r}
CoarseMemData$Congruency<-as.factor(CoarseMemData$Congruency)
levels(CoarseMemData$Congruency)<-c("Con","Incon")
CoarseMemData$StimVal<-as.factor(CoarseMemData$StimVal)
CoarseMemData$Action<-as.factor(CoarseMemData$Action)
CoarseMemData$Tprecise_bias<-as.numeric(as.character(CoarseMemData$Tprecise_bias))
CoarseMemData$Trun_bias<-as.numeric(as.character(CoarseMemData$Trun_bias))
CoarseMemData$Tprecise_biasabs<-as.numeric(as.character(CoarseMemData$Tprecise_biasabs))
CoarseMemData$Trun_biasabs<-as.numeric(as.character(CoarseMemData$Trun_biasabs))
```
Check number of participants
```{r}
length(unique(CoarseMemData$participant))
```


**Calculate individual chance level using permutation methods (DuBrow 2024)**
cleaned
```{r}
CoarseMemData_cor_clean <- CoarseMemData_clean %>%
  group_by(participant) %>%
  dplyr::summarize(
    pearson_r = cor(Treal_precise, Testimate_precise, method = "pearson", use = "complete.obs"),
    pearson_p = suppressWarnings(cor.test(Treal_precise, Testimate_precise, method = "pearson")$p.value),
    spearman_r = cor(Treal_precise, Testimate_precise, method = "spearman", use = "complete.obs"),
    spearman_p = suppressWarnings(cor.test(Treal_precise, Testimate_precise, method = "spearman")$p.value),
    .groups = "drop"
  )
mean(CoarseMemData_cor_clean$pearson_r)
 sd(CoarseMemData_cor_clean$pearson_r)
```
Plot the box-plot
```{r}
ggplot(CoarseMemData_cor_clean, aes(x = "", y = pearson_r)) +
  geom_boxplot(outlier.shape = NA, fill = "lightgray") +
  geom_jitter(width = 0.3, alpha = 0.6, color = "darkgray", size = 0.8) +
  labs(x = "",
       y = "Correlation (r)") +
  theme_classic(base_size=10.5)+
  theme(plot.title = element_blank())+
  labs(title="")+
  # theme(axis.text.y = element_text(size=rel(1)))+ 
    theme(axis.line = element_line(colour = 'black', size = 0.3))+
  theme(axis.ticks = element_line(colour = "black", size = 0.3))+
  theme(axis.text.x = element_blank(),       # ⬅️ remove x-axis labels
    axis.ticks.x = element_blank())+       # ⬅️ remove x-axis tick marks
  # theme(axis.title.x = element_blank())+
  scale_y_continuous(limits = c(0, 0.7),
                     expand = c(0, 0),
                     position = "left")
  # +coord_flip()

ggsave("YOURRESULTSDIR/Manuscripts/MemoryMS/Figures/RawPlots/ActCorrelationDistribution.pdf",height=2, width=1.2, dpi=300, device=cairo_pdf)
```

##plot histogram for actual and estimates time correlation 
```{r}
# Plot the histogram using ggplot2
ggplot(CoarseMemData_cor_clean, aes(y = ..density..,x = pearson_r)) +
  geom_histogram(binwidth = 0.03, fill = "#b3b3b3", color = "black", size = 0.1) +
  geom_vline(xintercept = mean(CoarseMemData_cor_clean$pearson_r), linetype = "solid", color = "#377EB8", size = 0.7) +  # # Add vertical line for mean correlation
  labs(x = "Correlation (r)\n Actual vs. Estimated Time", y = "Frequency") +
  theme_classic(base_size=11)+
  theme(plot.title = element_blank())+
  theme(axis.text.y = element_text(size=rel(1)))+ 
  # theme(axis.title.x = element_blank())+
  scale_y_continuous(expand = c(0,0), labels = scales::number_format(accuracy = 0.1))
  # scale_x_continuous(expand = c(0,0), limits = c(-0.25,0.25), labels = scales::number_format(accuracy = 0.1))

ggsave("YOURRESULTSDIR/Manuscripts/MemoryMS/Figures/RawPlots/DistributionActvsEstTime.pdf",height=4, width=3.5, dpi=300, device=cairo_pdf)
```
Permutation plot
##Plot a sample sub permutation
```{r}
sub=12
CoarseMemData_Per <- CoarseMemData[CoarseMemData$participant==sub,]
Per_r_Spearman <-c()
Per_p_Spearman <- c()
Per_r_Pearson <-c()
Per_p_Pearson <- c()
PerNum <- c()

for (i in 1:500){
  CoarseMemData_Per$Testimate_precise_per<-runif(nrow(CoarseMemData_Per), 0,8)
  Pearson_mod <- cor.test(CoarseMemData_Per$Treal_precise, CoarseMemData_Per$Testimate_precise_per,method = "pearson", use = "complete.obs")
  Per_r_Pearson <- append(Per_r_Pearson, Pearson_mod[["estimate"]][["cor"]])
  Per_p_Pearson <- append(Per_p_Pearson, Pearson_mod[["p.value"]])
  
  Spearman_mod <- cor.test(CoarseMemData_Per$Treal_precise, CoarseMemData_Per$Testimate_precise_per,method = "spearman", use = "complete.obs")
  Per_r_Spearman <- append(Per_r_Spearman, Spearman_mod[["estimate"]][["rho"]])
  Per_p_Spearman <- append(Per_p_Spearman, Spearman_mod[["p.value"]])
  
  PerNum <- append(PerNum, i)
}
Permdf <- data.frame(Per_r_Pearson, Per_p_Pearson, Per_r_Spearman, Per_p_Spearman, PerNum)

# Plot the histogram using ggplot2
ggplot(Permdf, aes(y = ..density..,x = Per_r_Pearson)) +
  geom_histogram(binwidth = 0.01, fill = "#b3b3b3", color = "black", size = 0.1) +
  geom_vline(xintercept = mean(CoarseMemData_cor_clean$pearson_r), linetype = "solid", color = "#377EB8", size = 0.7) +  # Add vertical line at -0.16
  geom_vline(xintercept = quantile(Permdf$Per_r_Pearson, 0.95), linetype = "dotted", color = "#377EB8", size = 0.7) + #chance level
  labs(x = "Correlation (r)", y = "Frequency") +
  theme_classic(base_size=18)+
  # theme(plot.title = element_blank())+
  labs(title = "")+
  theme(axis.text.y = element_text(size=rel(1)))+ 
    theme(axis.line = element_line(colour = 'black', size = 0.5))+
  theme(axis.ticks = element_line(colour = "black", size = 0.5))+
  # theme(axis.title.x = element_blank())+
  scale_y_continuous(expand = c(0,0))
  # scale_x_continuous(expand = c(0,0), limits = c(-0.25,0.25), labels = scales::number_format(accuracy = 0.1))

ggsave("YOURRESULTSDIR/Manuscripts/MemoryMS/Figures/RawPlots/PermutationPlot_meanCorr.pdf",height=4, width=3, dpi=300, device=cairo_pdf)
```

Get the group permutation r
```{r}
set.seed(123)

subs <- unique(CoarseMemData_clean$participant)

all_perm <- do.call(rbind, lapply(subs, function(sub){

  dat <- CoarseMemData_clean[CoarseMemData_clean$participant == sub, ]

  out <- data.frame(
    participant = sub,
    PerNum = 1:500,
    Per_r_Pearson  = NA_real_,
    Per_p_Pearson  = NA_real_,
    Per_r_Spearman = NA_real_,
    Per_p_Spearman = NA_real_
  )

  for (i in 1:500){
    dat$Testimate_precise_per <- runif(nrow(dat), 0, 8)

    pear <- cor.test(dat$Treal_precise, dat$Testimate_precise_per,
                     method="pearson", use="complete.obs")
    spear <- cor.test(dat$Treal_precise, dat$Testimate_precise_per,
                      method="spearman", use="complete.obs")

    out$Per_r_Pearson[i]  <- unname(pear$estimate)
    out$Per_p_Pearson[i]  <- pear$p.value
    out$Per_r_Spearman[i] <- unname(spear$estimate)
    out$Per_p_Spearman[i] <- spear$p.value
  }

  out
}))

# Group “chance level” by permutation number (mean across subjects at each PerNum)
group_chance <- aggregate(
  cbind(Per_r_Pearson, Per_r_Spearman) ~ PerNum,
  data = all_perm,
  FUN = mean,
  na.rm = TRUE
)

```
```{r}
# Plot the histogram using ggplot2
ggplot(group_chance, aes(y = ..density..,x = Per_r_Pearson)) +
  geom_histogram(binwidth = 0.001, fill = "#b3b3b3", color = "black", size = 0.01) +
  geom_vline(xintercept = mean(CoarseMemData_cor_clean$pearson_r), linetype = "solid", color = "#377EB8", size = 0.7) +  # Add vertical line at -0.16
  geom_vline(xintercept = quantile(group_chance$Per_r_Pearson, 0.95), linetype = "dotted", color = "#377EB8", size = 0.7) + #chance level
  labs(x = "Correlation (r)", y = "Frequency") +
  theme_classic(base_size=10.5)+
  theme(plot.title = element_blank())+
  theme(axis.text.y = element_text(size=rel(1)))+ 
    theme(axis.line = element_line(colour = 'black', size = 0.3))+
  theme(axis.ticks = element_line(colour = "black", size = 0.3))
  # theme(axis.title.x = element_blank())+
  scale_y_continuous(expand = c(0,0))
  # scale_x_continuous(expand = c(0,0), limits = c(-0.25,0.25), labels = scales::number_format(accuracy = 0.1))

ggsave("YOURRESULTSDIR/Manuscripts/MemoryMS/Figures/RawPlots/PermutationPlot_meanCorr_2.pdf",height=2.3, width=2.3, dpi=300, device=cairo_pdf)
```




##Plot histograms of confidence rating
```{r}
CoarseMemData_clean <- CoarseMemData_clean %>%
  mutate(ConfReconMem_num = case_when(
    ConfReconMem == "SConf_1" ~ 2,
    ConfReconMem == "ModConf_1" ~ 3,
    ConfReconMem == "VeryConf_1" ~ 4,
    ConfReconMem == "NotConfAtALL_1" ~ 1,
    TRUE ~ NA_real_
  ))
```
```{r}
CoarseMemData_clean <- CoarseMemData_clean %>%
  mutate(ConfCoarseMem_num = case_when(
    ConfCoarseMem == "SConf_2" ~ 2,
    ConfCoarseMem == "ModConf_2" ~ 3,
    ConfCoarseMem == "VeryConf_2" ~ 4,
    ConfCoarseMem == "NotConfAtALL_2" ~ 1,
    TRUE ~ NA_real_
  ))
```

```{r}
# Plot the histogram using ggplot2
ggplot(CoarseMemData_clean, aes(y = ..density..,x = ConfReconMem_num)) +
  geom_histogram(binwidth = 1, fill = "#b3b3b3", color = "black", size = 0.1) +
  # geom_vline(xintercept = mean(CoarseMemData_cor_clean$pearson_r), linetype = "solid", color = "#377EB8", size = 0.7) +  # # Add vertical line for mean correlation
  labs(x = "Confidence Rating", y = "Frequency") +
  theme_classic(base_size=11)+
  theme(plot.title = element_blank())+
  theme(axis.text.y = element_text(size=rel(1)))+ 
  # theme(axis.title.x = element_blank())+
  scale_y_continuous(expand = c(0,0), labels = scales::number_format(accuracy = 0.1))
  # scale_x_continuous(expand = c(0,0), limits = c(-0.25,0.25), labels = scales::number_format(accuracy = 0.1))

ggsave("YOURRESULTSDIR/Manuscripts/MemoryMS/Figures/RawPlots/ConfidenceInterval.pdf",height=2.3, width=2.3, dpi=300, device=cairo_pdf)
```
```{r}
# Plot the histogram using ggplot2
ggplot(CoarseMemData_clean, aes(y = ..density..,x = ConfCoarseMem_num)) +
  geom_histogram(binwidth = 1, fill = "#b3b3b3", color = "black", size = 0.1) +
  # geom_vline(xintercept = mean(CoarseMemData_cor_clean$pearson_r), linetype = "solid", color = "#377EB8", size = 0.7) +  # # Add vertical line for mean correlation
  labs(x = "Confidence Rating", y = "Frequency") +
  theme_classic(base_size=11)+
  theme(plot.title = element_blank())+
  theme(axis.text.y = element_text(size=rel(1)))+ 
  # theme(axis.title.x = element_blank())+
  scale_y_continuous(expand = c(0,0), labels = scales::number_format(accuracy = 0.1))
  # scale_x_continuous(expand = c(0,0), limits = c(-0.25,0.25), labels = scales::number_format(accuracy = 0.1))

ggsave("YOURRESULTSDIR/Manuscripts/MemoryMS/Figures/RawPlots/ConfidenceIntervalTimeLine.pdf",height=2.3, width=2.3, dpi=300, device=cairo_pdf)
```




