---
title: "AAfMRI_TRbyTR"
author: "Jingyi"
date: "Jan/21/2024"
output: pdf_document
---

```{r setup, include=FALSE}
rm(list=ls(all=TRUE)) 
library(afex)
library(emmeans)
library(knitr)
library(tidyverse)
library(compute.es)
library(car)
library(ggplot2)
library(multcomp)
library(pastecs)
library(WRS2)
library(Hmisc)
library(tidyverse)
library(SuppDists)
library(ggpubr)
library(readxl)
library(ez)
library(nlme)
library(dplyr)
library(pacman)
p_load(reshape2, viridis, hrbrthemes,MASS,gridExtra)
p_load(interactions)
p_load(plyr)
knitr::opts_chunk$set(echo = TRUE)
`select` <- dplyr::select
`recode` <- dplyr::recode
options(contrasts=c("contr.sum","contr.poly"))
```
set plot
set group regression plot
```{r}
myGroupCorrelation_group_sub <- function(datainit, completevar, Formula,  xvar, yvar, xlabel, ylabel, highcolor, modlinecolor, plottitle, fnamepdf, fnamepng, hjust){
  #Make sure all the rows contain values
  data <- datainit[complete.cases(datainit[[completevar]]), ]
  # Create predicted values based on the model
  tmp_ml <- lmer(Formula, data = data, REML =FALSE)
tmp_summary <- summary(tmp_ml)
tmp_anova <- anova(tmp_ml)
p_value <- tmp_anova$`Pr(>F)`[1]

  if (round(as.numeric(p_value),3) >= 0.001){
    labelnow <- paste( " p = ", round(as.numeric(p_value), digits=3))
    
  }
else if (round(as.numeric(p_value), 3) < 0.001){
  labelnow <- "p < 0.001"
}

#just to trick the plot. But need to find a better solution
tmp_ml <- lmer(Formula, data = data, REML = FALSE)
data$predictnum <- predict(tmp_ml,variances=list(fixef=TRUE,ranef=FALSE))

# Calculate the range for x and y
x_range <- range(data[[xvar]], na.rm = TRUE)
y_range <- range(data$predictnum, na.rm = TRUE)

# Calculate the y-values at the x limits of your data
intercept <- tmp_summary[["coefficients"]][1]
slope <- tmp_summary[["coefficients"]][2]

# Endpoints of the line
y_start <- slope * x_range[1] + intercept
y_end <- slope * x_range[2] + intercept

## Create a list of colors
# Extract participant list
pplst <- unique(data$sub)
nsub <- length(pplst)
# Define a list of colors from Blues (one per subject)
colour_lst2  <- scales::seq_gradient_pal(low = "#FCF5F2", high = highcolor, space = "Lab")(1:nsub/nsub)

# create values for scale colour manual (assign each color to a participant)
values_lst2 <- setNames(colour_lst2, pplst)

# create plot
pltnow <- ggplot(data,
                           aes(x = get(xvar),
                               y = predictnum,
                               color = factor(sub), group = factor(sub)))+
  geom_smooth(method = lm, se=F, size=0.3, alpha=0.5)+
  scale_color_manual(values = values_lst2)+
  # geom_abline(aes(intercept=`(Intercept)`, slope=get(xvar)), as.data.frame(t(fixef(tmp_ml))), lwd= 1,col = modlinecolor, size = 3) +
  geom_segment(aes(x = x_range[1], y = y_start, xend = x_range[2], yend = y_end), 
               lwd = 1, col = modlinecolor, size = 3) +
  # coord_cartesian(xlim = c(-2, 1)) +
  annotate("text", size= 4, x=Inf, y = Inf, label = labelnow,colour = "black",vjust=1.15, hjust=hjust)+
  ylab(ylabel)+
  xlab(xlabel)+
  theme_classic(base_size = 20) +
  
  theme(axis.title.y = element_text(size = rel(1), angle = 90,  vjust=1.25))+
  theme(axis.title.x = element_text(size = rel(1), angle = 0,  vjust=0))+
  theme(axis.text.x = element_text(size=rel(1)))+
  theme(axis.text.y = element_text(size=rel(1)))+
  theme(legend.position="none")+
  theme(axis.line = element_line(colour = 'black', size = 0.5))+
  theme(axis.ticks = element_line(colour = "black", size = 0.5))+
      theme(axis.title.y = element_text(size = rel(0.85), angle = 90,  vjust=1.25))+
  theme(axis.title.x = element_text(size = rel(0.85), angle = 0,  vjust=0))+
  theme(axis.text.x = element_text(size=rel(0.85)))+
  theme(axis.text.y = element_text(size=rel(0.85)))+
  scale_y_continuous(labels = scales::number_format(accuracy = 0.1,))+
  labs(title = plottitle)
        # panel.grid.major = element_blank(),
        # panel.grid.minor = element_blank())

pltnow

ggsave(fnamepdf, width = 4, height = 4,dpi=300)
ggsave(fnamepng, width = 4, height = 4, dpi = 600)
}
```



```{r}
myGroupCorrelation_group_nosub <- function(datainit, completevar, Formula,  xvar, yvar, xlabel, ylabel, highcolor, modlinecolor, plottitle, fnamepdf, fnamepng, hjust){
  #Make sure all the rows contain values
  data <- datainit[complete.cases(datainit[[completevar]]), ]
  # Create predicted values based on the model
  tmp_ml <- lmer(Formula, data = data, REML =FALSE)
tmp_summary <- summary(tmp_ml)
tmp_anova <- anova(tmp_ml)
p_value <- tmp_anova$`Pr(>F)`[1]

  if (round(as.numeric(p_value),3) >= 0.001){
    labelnow <- paste( " p = ", round(as.numeric(p_value), digits=3))
    
  }
else if (round(as.numeric(p_value), 3) < 0.001){
  labelnow <- "p < 0.001"
}

#just to trick the plot. But need to find a better solution
# fit model
tmp_ml <- lmer(Formula, data = data, REML = FALSE)

# prediction grid along xvar
  xseq <- seq(min(data[[xvar]], na.rm = TRUE),
              max(data[[xvar]], na.rm = TRUE), length.out = 100)
  
  # emmeans across xvar; this gives fixed-effects (population-level) line
  emm <- emmeans(tmp_ml,
                 specs = reformulate(xvar),                     # ~ xvar
                 at    = setNames(list(xseq), xvar))
  
  # get CIs explicitly
  emm_df <- as.data.frame(confint(emm, level = 0.95))
  # Normalize column names to a consistent set
  nm <- names(emm_df)
  if ("emmean" %in% nm) {
    names(emm_df)[names(emm_df) == "emmean"] <- "fit"
  } else if ("response" %in% nm) {
    names(emm_df)[names(emm_df) == "response"] <- "fit"
  } else if ("prob" %in% nm) {
    names(emm_df)[names(emm_df) == "prob"] <- "fit"
  }
  if ("lower.CL" %in% nm) {
    # ok
  } else if ("asymp.LCL" %in% nm) {
    names(emm_df)[names(emm_df) == "asymp.LCL"] <- "lower.CL"
  }
  if ("upper.CL" %in% nm) {
    # ok
  } else if ("asymp.UCL" %in% nm) {
    names(emm_df)[names(emm_df) == "asymp.UCL"] <- "upper.CL"
  }
  
  # safety check
  need_cols <- c(xvar, "fit", "lower.CL", "upper.CL")
  missing_cols <- setdiff(need_cols, names(emm_df))
  if (length(missing_cols)) {
    stop("Missing expected columns in emm_df: ", paste(missing_cols, collapse = ", "))
  }
  
  # build the plot explicitly
  pltnow <- ggplot(emm_df, aes(x = .data[[xvar]], y = .data[["fit"]])) +
    geom_line(linewidth = 1, color = modlinecolor) +
    geom_ribbon(aes(ymin = .data[["lower.CL"]], ymax = .data[["upper.CL"]]),
                alpha = 0.2, linewidth = 0, fill = modlinecolor) +

  annotate("text", size= 4, x=Inf, y = Inf, label = labelnow,colour = "black",vjust = 1, hjust=hjust)+
  ylab(ylabel)+
  xlab(xlabel)+
  theme_classic(base_size = 20.5) +
  
  theme(axis.title.y = element_text(size = rel(1), angle = 90,  vjust=1.25))+
  theme(axis.title.x = element_text(size = rel(1), angle = 0,  vjust=0))+
  theme(axis.text.x = element_text(size=rel(1)))+
  theme(axis.text.y = element_text(size=rel(1)))+
  theme(legend.position="none")+
  theme(axis.line = element_line(colour = 'black', size = 0.5))+
  theme(axis.ticks = element_line(colour = "black", size = 0.5))+
      theme(axis.title.y = element_text(size = rel(0.85), angle = 90,  vjust=1.25))+
  theme(axis.title.x = element_text(size = rel(0.85), angle = 0,  vjust=0))+
  theme(axis.text.x = element_text(size=rel(0.85)))+
  theme(axis.text.y = element_text(size=rel(0.85)))+
  labs(title = plottitle)
        # panel.grid.major = element_blank(),
        # panel.grid.minor = element_blank())

ggsave(fnamepdf, width = 3.5, height = 4,dpi=300)
ggsave(fnamepng, width = 3.5, height = 4, dpi = 600)
}
```



One factor
```{r}
barPlotOnefactor <- function(tmpdf, xvar, yvar, xlab, ylab, ymin, ymax, fnpdf, fnpng, negcolor, neucolor, height, width, digits){
ggplot(tmpdf , aes(x=get(xvar), y=get(yvar), fill = as.factor(get(xvar))))+
  geom_bar(position=position_dodge(.7), size=.75,  width=0.48, colour="black", stat= "identity", alpha = 0.8) +
  geom_errorbar(position=position_dodge(.7), size=.75, width=.1,
                aes(ymin=get(yvar)-se, ymax=get(yvar)+se)) + #VAR NAME plus minus SE
  theme_classic(base_size=20)+
  # scale_y_continuous(expand = c(0,0),limits = c(0,2.7))+
  coord_cartesian(ylim = c(ymin, ymax))+ # set the y limits
  ylab(ylab)+
  xlab(xlab)+
  labs(title = "")+
  scale_y_continuous(
  labels = scales::number_format(accuracy = digits,
                                 decimal.mark = '.'))+
  # labs(fill="Block change condition")+
  # theme(axis.title.y = element_text(size = rel(1), angle = 90,  vjust=1.25))+
  # theme(axis.title.x = element_text(size = rel(1), angle = 0,  vjust=0))+
  # theme(axis.text.x = element_text(size=rel(1)))+
  # theme(axis.text.y = element_text(size=rel(1)))+
  theme(legend.position = "none")+
    theme(axis.line = element_line(colour = 'black', size = 0.5))+
  theme(axis.ticks = element_line(colour = "black", size = 0.5))+
      theme(axis.title.y = element_text(size = rel(0.85), angle = 90,  vjust=1.25))+
  theme(axis.title.x = element_text(size = rel(0.85), angle = 0,  vjust=0))+
  theme(axis.text.x = element_text(size=rel(0.85)))+
  theme(axis.text.y = element_text(size=rel(0.85)))+ 
  #annotate("text", size= 4, x=2.3,  y = 1.75, label = "bars=SEM",  colour = "black")+
  # from set 1 color brewer
  scale_fill_manual(values=c(negcolor, neucolor, "#FB8072","#CC0033","#66C2A5","#339999","#66CC66", "#990033", "#FFFFCC","#FF9999","#FFFF00"))
  # scale_x_discrete(name="Border Color",labels=c("No Change", "Change"))# usual red: "#FC8D62"
  # guides(fill = guide_legend(override.aes = list(colour = NULL))) +
  # theme(legend.key.width=unit(1,"line"),legend.key.height=unit(1,"line"),legend.text=element_text(size = 16))++theme( legend.position="right")
#guides(fill=FALSE)
ggsave(fnpdf,height=height, width=width, dpi=300, device=cairo_pdf) 
ggsave(fnpng,height=height, width=width, dpi = 600)
}
```


```{r}
# Function to replace strings
transform_string <- function(s){
  s = gsub("harvardoxford_Hippocampus_bin60_2mm_Anterior", "aHPC", s)
  s = gsub("harvardoxford_Hippocampus_bin60_2mm_Mid", "midHPC", s)
  s = gsub("harvardoxford_Hippocampus_bin60_2mm_Posterior", "pHPC", s)
  s = gsub("harvardoxford_Hippocampus_bin60_2mm", "HPC", s)
  s = gsub("FS_entorhinal_exvivo.thresh", "Entorhinal", s)
  s = gsub("BA4_exvivo.thresh", "BA4", s)
  s = gsub("V1_exvivo.thresh", "V1", s)
  s = gsub("FS_", "", s)
  s = gsub("Amy_50_bin", "Amygdala", s)
  s = gsub("Amy_bin50_2mm", "Amygdala", s)
  s = gsub("AMY", "Amygdala", s)
  s = gsub("_2mm", "", s)
  s = gsub("lh.L_", "Left ", s)
  s = gsub("rh.R_", "Right ", s)  
    s = gsub("L_", "Left ", s)
  s = gsub("R_", "Right ", s)
  s = gsub("perirhinal_exvivo.thresh", "PRC", s)
  s = gsub("uni_", "", s)
  # s = gsub("_", " ", s)
  return (s)  
}
```
to grab SE scripts
```{r}
pathnames <- list.files(pattern="[.]R$", path="/Users/jingyiwang/Dropbox/LEAP_Neuro_Lab/resources/R/Rfunctions/", full.names=TRUE);
sapply(pathnames, FUN=source);
```

Set color
```{r}
library("colorspace")
# hcl_palettes(plot = TRUE)
BR<-diverging_hcl(5, palette = "Blue-Red 2")
allcolor<-c(BR[1], BR[5], BR[2], BR[4])

colorList1 <- c(sequential_hcl(7, palette = "Mint"))
colorList2 <- c(sequential_hcl(7, palette = "Peach"))

colorList3 <- c(sequential_hcl(5, palette = "Reds"))
colorList4 <- c(sequential_hcl(5, palette = "Blues"))

list_2color <- c(colorList2[3], colorList1[3])
list_2color_1 <- c(colorList2[2], colorList1[2])

list_2color_2 <- c(colorList3[3], colorList4[2])
 
# Failcolor <- allcolor[5]
# Succcolor <- allcolor[1]

negcolor <- list_2color[1]
poscolor <- list_2color[2]

Failcolor <- list_2color_2[1]
Succcolor <- list_2color_2[2]

regressline <- "#424242" #another option: "#7F7EBC"; "#86BFDE"
ribbonline <- "#BEBEBE"
"#7F7EBC"
"#86BFDE"
"#E1E1E1"
"#BEBEBE"
highcolor <- sequential_hcl(5, palette = "Grays")[3]

HPCcolor <- "#95BBD8"
PRCcolor <- "#54D388"
FPlcolor <- "#B64097"
```
Merge dataframe from different masks and loop through masks
```{r}
# Set working directory to source file location
setwd("YOURRESULTSDIR/TRbyTR/RSAbymaskNew")

# Load the data
HPC <- read_csv("harvardoxford_Hippocampus_bin60_2mm_all_rsas_TRbyTR_trialwise_extended.csv")
length(unique(HPC$sub))
#Remove sub 007 013, since bad motion
HPC <- HPC[!HPC$sub %in% c("007", "013","027", "081", "066", "057"),]
length(unique(HPC$sub))

aHPC <- read_csv("harvardoxford_Hippocampus_bin60_2mm_Anterior_all_rsas_TRbyTR_trialwise_extended.csv")
#Remove sub 007 013, since bad motion
aHPC <- aHPC[!aHPC$sub %in% c("007", "013","027", "081", "066", "057"),]


pHPC <- read_csv("harvardoxford_Hippocampus_bin60_2mm_Posterior_all_rsas_TRbyTR_trialwise_extended.csv")
# Remove sub 007 013, since bad motion
pHPC <- pHPC[!pHPC$sub %in% c("007", "013","027", "081", "066", "057"),]


midHPC <- read_csv("harvardoxford_Hippocampus_bin60_2mm_Mid_all_rsas_TRbyTR_trialwise_extended.csv")
#Remove sub 007 013, since bad motion
midHPC <- midHPC[!midHPC$sub %in% c("007", "013","027", "081", "066", "057"),]


AMY <- read_csv("Amy_50_bin_all_rsas_TRbyTR_trialwise_extended.csv")
#Remove sub 007 013, since bad motion
AMY <- AMY[!AMY$sub %in% c("007", "013", "027", "081", "066", "057"),]

Ent <- read_csv("FS_entorhinal_exvivo.thresh_all_rsas_TRbyTR_trialwise_extended.csv")
#Remove sub 007 013, since bad motion
Ent <- Ent[!Ent$sub %in% c("007", "013", "027", "081", "066", "057"),]

midPFC <- read_csv("9-46_all_rsas_TRbyTR_trialwise_extended.csv")
#Remove sub 007 013, since bad motion
midPFC <- midPFC[!midPFC$sub %in% c("007", "013", "027", "081", "066", "057"),]

midPFCd <- read_csv("9-46d_all_rsas_TRbyTR_trialwise_extended.csv")
#Remove sub 007 013, since bad motion
midPFCd <- midPFCd[!midPFCd$sub %in% c("007", "013", "027", "081", "066", "057"),]

midPFCv <- read_csv("9-46v_all_rsas_TRbyTR_trialwise_extended.csv")
#Remove sub 007 013, since bad motion
midPFCv <- midPFCv[!midPFCv$sub %in% c("007", "013", "027", "081", "066", "057"),]

BA4 <- read_csv("BA4_exvivo.thresh_all_rsas_TRbyTR_trialwise_extended.csv")
#Remove sub 007 013, since bad motion
BA4 <- BA4[!BA4$sub %in% c("007", "013", "027", "081", "066", "057"),]

FPl <- read_csv("FS_FPl_all_rsas_TRbyTR_trialwise_extended.csv")
#Remove sub 007 013, since bad motion
FPl <- FPl[!FPl$sub %in% c("007", "013", "027", "081", "066", "057"),]

FPm <- read_csv("FPm_all_rsas_TRbyTR_trialwise_extended.csv")
#Remove sub 007 013, since bad motion
FPm <- FPm[!FPm$sub %in% c("007", "013", "027", "081", "066", "057"),]


FP <- read_csv("FP_all_rsas_TRbyTR_trialwise_extended.csv")
#Remove sub 007 013, since bad motion
FP <- FP[!FP$sub %in% c("007", "013", "027", "081", "066", "057"),]

PMd <- read_csv("PMd_all_rsas_TRbyTR_trialwise_extended.csv")
#Remove sub 007 013, since bad motion
PMd <- PMd[!PMd$sub %in% c("007", "013", "027", "081", "066", "057"),]

V1 <- read_csv("V1_exvivo.thresh_all_rsas_TRbyTR_trialwise_extended.csv")
#Remove sub 007 013, since bad motion
V1 <- V1[!V1$sub %in% c("007", "013", "027", "081", "066", "057"),]

M1 <- read_csv("M1_all_rsas_TRbyTR_trialwise_extended.csv")
#Remove sub 007 013, since bad motion
M1 <- M1[!M1$sub %in% c("007", "013", "027", "081", "066", "057"),]

PRC <- read_csv("perirhinal_exvivo.thresh_all_rsas_TRbyTR_trialwise_extended.csv")
#Remove sub 007 013, since bad motion
PRC <- PRC[!PRC$sub %in% c("007", "013", "027", "081", "066", "057"),]

BA25 <- read_csv("25_all_rsas_TRbyTR_trialwise_extended.csv")
#Remove sub 007 013, since bad motion
BA25 <- BA25[!BA25$sub %in% c("007", "013", "027", "081", "066", "057"),]
BA25$mask <- as.character(BA25$mask)

BA32 <- read_csv("32pl_all_rsas_TRbyTR_trialwise_extended.csv")
#Remove sub 007 013, since bad motion
BA32 <- BA32[!BA32$sub %in% c("007", "013", "027", "081", "066", "057"),]
```

Merge
```{r}
# myDataAll <- dplyr::bind_rows(aHPC, midHPC, pHPC, HPC, AMY, FPl, Ent, RaHPC, RpHPC, RmidHPC, RHPC, RAMY, LaHPC, LpHPC, LmidHPC, LHPC, LAMY, RBLcx, LBLcx, BLcx)
myDataAll <- dplyr::bind_rows(aHPC, midHPC, pHPC, HPC, AMY, FPl, Ent, midPFC, midPFCd, midPFCv, PMd, V1, FP, FPm, BA4, M1, PRC, BA25, BA32)
nrow(myDataAll)
```

add a column for TR pairs
```{r}
myDataAll$TRpairs <- paste(myDataAll$TR1, myDataAll$TR2, sep="_")
```
Set factors
```{r}
myDataAll$TRpairs <- as.factor(as.character(myDataAll$TRpairs))
myDataAll$aromn <- as.numeric(myDataAll$aromn)
myDataAll$valmn <- as.numeric(myDataAll$valmn)
myDataAll$StimVal <- as.factor(myDataAll$StimVal)
myDataAll$PerciseBiasFlag <- as.factor(myDataAll$PerciseBiasFlag)
myDataAll$PercisepChanceFlag <- as.factor(myDataAll$PercisepChanceFlag)
myDataAll$RunBias1Flag <- as.factor (myDataAll$RunBias1Flag)
myDataAll$RunBias2Flag <- as.factor(myDataAll$RunBias2Flag)
myDataAll$sub <- as.numeric(as.character(myDataAll$sub))
myDataAll$ReconMem <- as.factor(myDataAll$ReconMem)
levels(myDataAll$ReconMem) <- c("Recognized", "Forgotten")
```

add actiongoal column
```{r}
myDataAll <- myDataAll %>% mutate(ActionGoal = case_when(condition == "neg_app" ~ "Apporach", condition == "pos_app" ~ "Apporach", condition == "neg_avoid" ~ "Avoid", condition == "pos_avoid" ~ "Avoid"))
myDataAll$ActionGoal <- as.factor(myDataAll$ActionGoal)
```
add order_final column
```{r}
myDataAll <- myDataAll %>% mutate(order_final = case_when(order == 1 & sub%%2==0 ~ 1, order == 1 & sub%%2!=0 ~ 2, order == 2 & sub%%2==0 ~ 3, order == 2 & sub%%2!=0 ~ 4, order == 5 & sub%%2==0 ~ 5, order == 5 & sub%%2!=0 ~ 6, order == 6 & sub%%2==0 ~ 7, order == 6 & sub%%2!=0 ~ 8))
myDataAll$order_final <- as.factor(myDataAll$order_final)
```
**Add the TempMem sign flag**
```{r}
myDataAll <- myDataAll %>% mutate(TempMem_sign = case_when(Tprecise_bias < 0 ~ -1, Tprecise_bias > 0 ~ 1))
myDataAll$TempMem_sign <- as.factor(myDataAll$TempMem_sign)
levels(myDataAll$TempMem_sign) <- c("End", "Beginning")
```

**reverse the Tprecise_bias so that Estimates - Actual position**
Larger bias -> towards End
Smaller bias -> towards beginning
```{r}
myDataAll$Tprecise_bias <- (-1) * myDataAll$Tprecise_bias
```

**Add the TrealCat: Early, Mid, Late**
```{r}
myDataAll <- myDataAll %>%
  group_by(sub) %>%
  mutate(
    TrealCat = case_when(
      Treal_precise <= quantile(Treal_precise, 1/3, na.rm = TRUE) ~ "Early",
      Treal_precise <= quantile(Treal_precise, 2/3, na.rm = TRUE) ~ "Mid",
      TRUE ~ "Late"
    )
  ) %>%
  ungroup()

myDataAll$TrealCat <- as.factor(myDataAll$TrealCat)
levels(myDataAll$TrealCat)
```


Add the Img parameters
```{r}
setwd("YOURRESULTSDIR/LumCal/ASAPstim")
# lum <- read.table("img_statistics.txt", header = TRUE)
lum <- read.delim("img_statistics.txt", sep = "\t", header = TRUE)
```
```{r}
#remove .jpg
lum$Img <- sub("\\.jpg$", "", lum$Img)

# Rename the column to 'ImgStim'
names(lum)[names(lum) == "Img"] <- "ImgStim"
```

Merge
```{r}
nrow(myDataAll)
myDataAll <- dplyr::left_join(myDataAll, lum, by=c("ImgStim"))
nrow(myDataAll)
myDataAll$lum_rgb <- as.numeric (myDataAll$lum_rgb)
```

##Load univariate betas with pre-whitten values
```{r}
HPC_whitten <- read.csv("YOURRESULTSDIR/AMY_uni/harvardoxford_Hippocampus_bin60_2mm_univariate.csv")
HPC_whitten<- HPC_whitten[HPC_whitten$mask=="harvardoxford_Hippocampus_bin60_2mm",]
nrow(HPC_whitten)
PRC_whitten <- read.csv("YOURRESULTSDIR/AMY_uni/perirhinal_exvivo.thresh_univariate.csv")
PRC_whitten <- PRC_whitten[PRC_whitten$mask=="perirhinal_exvivo.thresh",]
nrow(PRC_whitten)
AMY_whitten <- read.csv("YOURRESULTSDIR/AMY_uni/Amy_50_bin_univariate.csv")
AMY_whitten <- AMY_whitten[AMY_whitten$mask=="Amy_50_bin",]
nrow(AMY_whitten)
FPl_whitten <- read.csv("YOURRESULTSDIR/AMY_uni/FPl_univariate.csv")
FPl_whitten <- FPl_whitten[FPl_whitten$mask=="FPl",]
nrow(FPl_whitten)
```
Merge
```{r}
nrow(myDataAll)
colnames(HPC_whitten) <- c("sub", "mask", "run", "trial", "ImgStim", "value_HPC", "uni_whiten_HPC")
HPC_whitten <- HPC_whitten %>% select("sub", "run", "trial", "ImgStim", "uni_whiten_HPC")
# HPC_whitten$trial <- as.factor(HPC_whitten$trial)
myDataAll <- dplyr::left_join(myDataAll, HPC_whitten, by = c("sub", "run", "trial", "ImgStim"))
nrow(myDataAll)

colnames(AMY_whitten) <- c("sub", "mask", "run", "trial", "ImgStim", "value_AMY", "uni_whiten_AMY")
AMY_whitten <- AMY_whitten %>% select("sub", "run", "trial", "ImgStim", "uni_whiten_AMY")
# AMY_whitten$trial <- as.factor(AMY_whitten$trial)
myDataAll <- dplyr::left_join(myDataAll, AMY_whitten, by = c("sub", "run", "trial", "ImgStim"))
nrow(myDataAll)

colnames(PRC_whitten) <- c("sub", "mask", "run", "trial", "ImgStim", "value_PRC", "uni_whiten_PRC")
PRC_whitten <- PRC_whitten %>% select("sub", "run", "trial", "ImgStim", "uni_whiten_PRC")
# PRC_whitten$trial <- as.factor(PRC_whitten$trial)
myDataAll <- dplyr::left_join(myDataAll, PRC_whitten, by = c("sub", "run", "trial", "ImgStim"))
nrow(myDataAll)

colnames(FPl_whitten) <- c("sub", "mask", "run", "trial", "ImgStim", "value_FPl", "uni_whiten_FPl")
FPl_whitten <- FPl_whitten %>% select("sub", "run", "trial", "ImgStim", "uni_whiten_FPl")
# FPl_whitten$trial <- as.factor(FPl_whitten$trial)
myDataAll <- dplyr::left_join(myDataAll, FPl_whitten, by = c("sub", "run", "trial", "ImgStim"))
nrow(myDataAll)
```

**Add Temporal Memory filter column**
```{r}
TempMemppBad <- c(5, 6, 11, 13, 30, 36, 38, 53, 54, 64)
myDataAll <- myDataAll %>%
  mutate(
    TempMemfilter = if_else(sub %in% TempMemppBad, 0, 1)
  )

myDataAll_memfiltered <- myDataAll[myDataAll$TempMemfilter != 0,]
length(unique(myDataAll_memfiltered$sub))
```


**Get behaviral results here**
Create Bev data
```{r}
myDatabev <- myDataAll %>% group_by(sub, run, trial) %>% dplyr::summarize(CDA.ISCRsqrtcheck = first(CDA.ISCRsqrt), CDA.ISCRsqrt = mean(CDA.ISCRsqrt, na.rm=TRUE), StimVal = first(StimVal), ActionGoal = first(ActionGoal), Tprecise_biasabs = first(Tprecise_biasabs), Tprecise_bias = first(Tprecise_bias), order_final = first(order_final), uni_whiten_AMY = first(uni_whiten_AMY), uni_whiten_HPC = first(uni_whiten_HPC), uni_whiten_PRC = first(uni_whiten_PRC), uni_whiten_EC = first(uni_whiten_EC), uni_whiten_FPl = first(uni_whiten_FPl), ReconMem = first(ReconMem), ConfReconMem = first(ConfReconMem), ConfCoarseMem = first(ConfCoarseMem), valmn = first(valmn), aromn = first(aromn), CDA_tonicsqrt = first(CDA_tonicsqrt), TempMem_sign = first(TempMem_sign), Treal_precise = first(Treal_precise), TrealCat = first(TrealCat))
myDatabev_memfiltered <- myDatabev[!myDatabev$sub %in% TempMemppBad,]
```

```{r}
myDataAll$TrealCat <- fct_relevel(
  myDataAll$TrealCat,
  "Early", "Mid", "Late"
)

myDataAll_memfiltered$TrealCat <- fct_relevel(
  myDataAll_memfiltered$TrealCat,
  "Early", "Mid", "Late"
)
```


##Emotion influence on temporal memory
```{r}
tmpmod <- lmer(Tprecise_biasabs~valmn+ActionGoal+ ActionGoal+order_final+ (valmn|sub), data=myDatabev_memfiltered, REML =FALSE)
summary(tmpmod)
anova(tmpmod)
```

```{r}
tmpmod <- lmer(Tprecise_biasabs~valmn*ActionGoal+ ActionGoal+order_final+ (valmn|sub), data=myDatabev_memfiltered, REML =FALSE)
summary(tmpmod)
anova(tmpmod)
```

```{r}
tmpmod <- lmer(Tprecise_biasabs~valmn+ActionGoal+ ActionGoal+order_final+ ReconMem + (valmn|sub), data=myDatabev_memfiltered, REML =FALSE)
summary(tmpmod)
anova(tmpmod)
```

directional temporal memory
```{r}
tmpmod <- lmer(Tprecise_bias~valmn+aromn + ActionGoal+order_final+ (valmn|sub), data=myDatabev_memfiltered, REML =FALSE)
summary(tmpmod)
anova(tmpmod)
```
```{r}
tmpmod <- lmer(Tprecise_bias~valmn+aromn + ReconMem + ActionGoal+order_final+ (valmn|sub), data=myDatabev_memfiltered, REML =FALSE)
summary(tmpmod)
anova(tmpmod)
```

plot
```{r}
fnamepdf<-"YOURRESULTSDIR/Figures/RawPlots/valmnTempMem.pdf"
fnamepng<-"YOURRESULTSDIR/Figures/RawPlots/valmnTempMem.png"

xlabel<-"Normative Valence Rating"
ylabel<- "Temporal Memory Error (abs)"
plotTitle <- ""

myGroupCorrelation_group_nosub(myDatabev_memfiltered, "Tprecise_biasabs", "Tprecise_biasabs~valmn+aromn + ActionGoal+order_final+ (valmn|sub)", "valmn", "Tprecise_biasabs", xlabel, ylabel, highcolor, regressline, plotTitle, fnamepdf, fnamepng, 1.4)
```
plot
```{r}
fnamepdf<-"YOURRESULTSDIR/Figures/RawPlots/aromnTempMem.pdf"
fnamepng<-"YOURRESULTSDIR/Figures/RawPlots/aromnTempMem.png"

xlabel<-"Normative Arousal Rating"
ylabel<- "Temporal Memory Error (abs)"
plotTitle <- ""

myGroupCorrelation_group_nosub(myDatabev_memfiltered, "Tprecise_biasabs", "Tprecise_biasabs~aromn + valmn + ActionGoal+order_final+ (valmn|sub)", "aromn", "Tprecise_biasabs", xlabel, ylabel, highcolor, regressline, plotTitle, fnamepdf, fnamepng, 1.4)
```


```{r}
tmpmod <- lmer(Tprecise_biasabs~valmn*aromn + ActionGoal+order_final+ (valmn|sub), data=myDatabev_memfiltered, REML =FALSE)
summary(tmpmod)
anova(tmpmod)
```

Plot interaction
```{r}
#plot interaction
fname = "YOURRESULTSDIR/Figures/RawPlots/Interaction_ValmnAromn_Bias.pdf"
ylabel = "Temporal Memory Error (abs)"
#Plot it
interact_plot(tmpmod, pred=aromn, modx = valmn, x.label = "Normative Arousal Rating", y.label = ylabel, interval = TRUE,  line.thickness = 1, int.type = "confidence", 
              legend.main = "Normative Valence",
              legend.labels = c("Positive", "Mean", "Negative"), colors = c(negcolor, "#93C5DE", poscolor))+ theme_classic(18)+ scale_linetype_manual(values = c("solid", "solid", "solid"))+
      theme(axis.line = element_line(colour = 'black', size = 0.5))+
  theme(axis.ticks = element_line(colour = "black", size = 0.5))+
      theme(axis.title.y = element_text(size = rel(0.85), angle = 90,  vjust=1.25))+
  theme(axis.title.x = element_text(size = rel(0.85), angle = 0,  vjust=0))+
  theme(axis.text.x = element_text(size=rel(0.85)))+
  theme(axis.text.y = element_text(size=rel(0.85)))+
    theme(legend.title = element_text(size = rel(0.85)), legend.text = element_text(size = rel(0.65)))

ggsave(fname,height=3.5, width=6, dpi=300, device=cairo_pdf)
```


##Emotional effect on item memory 
```{r}
myDatabev_memfiltered <- myDatabev_memfiltered %>%
  mutate(ReconMemNum = ifelse(ReconMem == "Forgotten", 0, 1))
myDatabev <- myDatabev %>%
  mutate(ReconMemNum = ifelse(ReconMem == "Forgotten", 0, 1))
```


```{r}
tmpmod <- glmer(ReconMemNum ~ aromn+ ActionGoal+order_final+ (valmn|sub), data=myDatabev,family = binomial)
summary(tmpmod)
car::Anova(tmpmod, type=3)
```

plot
```{r}
fnamepdf<-"YOURRESULTSDIR/Figures/RawPlots/aromnReconMem.pdf"
fnamepng<-"YOURRESULTSDIR/Figures/RawPlots/aromnReconMem.png"

xlabel<-"Normative Arousal Rating"
ylabel<- "Probability of Remembering"
plotTitle <- ""

myGroupCorrelation_group_nosub_glmer(myDatabev, "ReconMemNum", "ReconMemNum ~ aromn+ ActionGoal+order_final+ (valmn|sub)", "aromn", "ReconMemNum", xlabel, ylabel, highcolor, regressline, plotTitle, fnamepdf, fnamepng, 1)
```

```{r}
tmpmod <- glmer(ReconMemNum ~ valmn+ ActionGoal+order_final+ (valmn|sub), data=myDatabev,family = binomial)
summary(tmpmod)
car::Anova(tmpmod, type=3)
```
plot
```{r}
fnamepdf<-"YOURRESULTSDIR/Figures/RawPlots/valmnReconMem.pdf"
fnamepng<-"YOURRESULTSDIR/Figures/RawPlots/valmnReconMem.png"

xlabel<-"Normative Valence Rating"
ylabel<- "Probability of Remembering"
plotTitle <- ""

myGroupCorrelation_group_nosub_glmer(myDatabev, "ReconMemNum", "ReconMemNum ~ valmn+ ActionGoal+order_final+ (valmn|sub)", "valmn", "ReconMemNum", xlabel, ylabel, highcolor, regressline, plotTitle, fnamepdf, fnamepng, 1)
```


##Relationship between Item memory and Temporal Memory
percent of remember
```{r}
groupdf <- myDatabev %>% group_by(sub) %>% dplyr::summarize(Percent=mean(ReconMem=="Recognized", na.rm=TRUE))
mean(groupdf$Percent)
sd(groupdf$Percent)
```

```{r}
tmpmod <- lmer(Tprecise_biasabs~ ReconMem + valmn + aromn + ActionGoal+order_final+ (valmn|sub), data=myDatabev_memfiltered,REML =FALSE)
summary(tmpmod)
anova(tmpmod)
```
plot
```{r}
"#6D6E71"
"#BCBEC0"
library(dplyr)
groupdf<-myDatabev_memfiltered %>% group_by(sub, ReconMem)%>%dplyr::summarize(Tprecise_biasabs = mean(Tprecise_biasabs, na.rm=TRUE))
detach("package:dplyr", force=TRUE)
sumdf <- summarySEwithin(groupdf, measurevar="Tprecise_biasabs", idvar="sub",withinvars=c("ReconMem"), na.rm=TRUE, conf.interval=.95)
xlab = "Item Memory"
ylab = "Temporal Memory Error (abs)"
ymin = min(sumdf$Tprecise_biasabs) - 4*max(sumdf$se)
ymax =  max(sumdf$Tprecise_biasabs) + 4*max(sumdf$se)
fnpdf = "YOURRESULTSDIR/Figures/RawPlots/TempMemvsItemMem.pdf"
fnpng = "YOURRESULTSDIR/Figures/RawPlots/TempMemvsItemMem.png"
barPlotOnefactor(sumdf, "ReconMem", "Tprecise_biasabs", xlab, ylab, ymin, ymax, fnpdf,fnpng, "#FFFFFF", "#6D6E71", height = 4, width= 3.4, 0.1)
```


Frequency plot for Item memory
```{r}
# Plot the histogram using ggplot2
ggplot(myDatabev, aes(y = ..density..,x = ConfReconMem)) +
  geom_histogram(binwidth = 1, fill = "#b3b3b3", color = "black", size = 0.1) +
  labs(x = "Item Memory Confidence", y = "Frequency") +
  theme_classic(base_size=11)+
  # theme(plot.title = element_blank())+
  theme(axis.text.y = element_text(size=rel(1)))+ 
  labs(title = "All trials")+
  # theme(axis.title.x = element_blank())+
  scale_y_continuous(expand = c(0,0), labels = scales::number_format(accuracy = 0.1))
  # scale_x_continuous(expand = c(0,0), limits = c(-0.25,0.25), labels = scales::number_format(accuracy = 0.1))

ggsave("YOURRESULTSDIR/Figures/RawPlots/ItemMemConfDistribution.pdf",height=2.3, width=2.3, dpi=300, device=cairo_pdf)
```

### TempMem ~ Item memory strength * TrealCat (session time)
```{r}
myDatabev_memfiltered_recon <- myDatabev_memfiltered[myDatabev_memfiltered$ReconMem == "Remembered",]
myDatabev_memfiltered_recon$TrealCat <-
  factor(myDatabev_memfiltered_recon$TrealCat,
         levels = c("Late", "Mid", "Early"))
tmpmod <- lmer(Tprecise_biasabs~ ConfReconMem*TrealCat + valmn + aromn + ActionGoal+order_final+ (valmn + ActionGoal|sub), data=myDatabev_memfiltered_recon,REML =FALSE)
summary(tmpmod)
anova(tmpmod)
```
test coeffient significance
```{r}
trends <- lstrends(tmpmod, pairwise ~ TrealCat, var = "ConfReconMem", pbkrtest.limit = 12552)
summary(trends)
```
```{r}
# Extract estimated trends
trends_estimates <- trends$lstrends

# Test if the slopes are significantly different from 0
tests <- test(trends_estimates)
tests
# Summarize the tests to get p-values
summary(tests)
```
```{r}
#plot interaction
fname = "YOURRESULTSDIR/Figures/RawPlots/Interaction_RealTime_TempBiasabsConfMem.pdf"
ylabel = "Temporal Memory Error (abs)"
#Plot it
p <- interact_plot(tmpmod, pred=ConfReconMem, modx = TrealCat,
              modx.values = c("Early","Mid","Late"),  legend = "Session Time", x.label = "Item Memory Confidence", y.label = ylabel, interval = TRUE,  line.thickness = 1,linetypes = rep("solid", 3), int.type = "confidence", colors = c("#C8E5CC", "#9FCDB1", "#12AD4B"))+ theme_classic(20)+
scale_linetype_manual(values = c("solid", "solid", "solid"))+
  
  theme(axis.title.y = element_text(size = rel(1), angle = 90,  vjust=1.25))+
  theme(axis.title.x = element_text(size = rel(1), angle = 0,  vjust=0))+
  theme(axis.text.x = element_text(size=rel(1)))+
  theme(axis.text.y = element_text(size=rel(1)))+
  theme(axis.line = element_line(colour = 'black', size = 0.5))+
  theme(axis.ticks = element_line(colour = "black", size = 0.5))+
      theme(axis.title.y = element_text(size = rel(0.85), angle = 90,  vjust=1.25))+
  theme(axis.title.x = element_text(size = rel(0.85), angle = 0,  vjust=0))+
  theme(axis.text.x = element_text(size=rel(0.85)))+
  theme(axis.text.y = element_text(size=rel(0.85)))+
  scale_y_continuous(labels = scales::number_format(accuracy = 0.1,))+
  labs(title = "")

ggsave(fname,height=4, width=6, dpi=300, device=cairo_pdf)
```

##Confidence level for temporal memory and item memory
```{r}
describe(myDataAll_memfiltered$ConfCoarseMem)
describe(myDataAll_memfiltered$ConfReconMem)
```
```{r}
sumdf <- myDataAll_memfiltered %>% 
  group_by(ConfCoarseMem) %>% 
  dplyr::summarise(n = n()) %>% 
  mutate(percent = 100 * n / sum(n))
```

```{r}
sumdf <- myDataAll_memfiltered %>% 
  group_by(ConfReconMem) %>% 
  dplyr::summarise(n = n()) %>% 
  mutate(percent = 100 * n / sum(n))
```


Temporal memroy confidence distribution
```{r}
# Plot the histogram using ggplot2
ggplot(myDataAll_memfiltered, aes(y = ..density..,x = ConfCoarseMem)) +
  geom_histogram(binwidth = 1, fill = "#b3b3b3", color = "black", size = 0.1) +
  labs(x = "Temporal Memory Confidence", y = "Frequency") +
  theme_classic(base_size=11)+
  # theme(plot.title = element_blank())+
  theme(axis.text.y = element_text(size=rel(1)))+ 
  labs(title = "All trials")+
  # theme(axis.title.x = element_blank())+
  scale_y_continuous(expand = c(0,0), labels = scales::number_format(accuracy = 0.1))
  # scale_x_continuous(expand = c(0,0), limits = c(-0.25,0.25), labels = scales::number_format(accuracy = 0.1))

ggsave("YOURRESULTSDIR/Figures/RawPlots/TempMemConfDistribution.pdf",height=2.3, width=2.4, dpi=300, device=cairo_pdf)
```


##Relationship between amygdala activation and emotion
```{r}
tmpmod <- lmer(uni_whiten_AMY ~ valmn + aromn +ActionGoal+order_final+ (valmn + ActionGoal|sub), data=myDatabev, REML =FALSE)
summary(tmpmod)
anova(tmpmod)
```
```{r}
fnamepdf<-"YOURRESULTSDIR/Figures/RawPlots/uni_whiten_AMY_Valmn.pdf"
fnamepng<-"YOURRESULTSDIR/Figures/RawPlots/uni_whiten_AMY_Valmn.png"
# "#2859BB"
# '#1627BB'

ylabel<-"Amygdala Activation"
xlabel<-"Normative Valence Rating"
plotTitle <- ""

myGroupCorrelation_group_nosub(myDatabev, "uni_whiten_AMY", "uni_whiten_AMY ~ valmn + aromn +ActionGoal+order_final+ (valmn + ActionGoal|sub)","valmn","uni_whiten_AMY",  xlabel, ylabel, highcolor, "#424242", plotTitle, fnamepdf, fnamepng, 1)
```

```{r}
fnamepdf<-"YOURRESULTSDIR/Figures/RawPlots/uni_whiten_AMY_Aromn.pdf"
fnamepng<-"YOURRESULTSDIR/Figures/RawPlots/uni_whiten_AMY_Aromn.png"
# "#2859BB"
# '#1627BB'

ylabel<-"Amygdala Activation"
xlabel<-"Normative Arousal Rating"
plotTitle <- ""

myGroupCorrelation_group_nosub(myDatabev, "uni_whiten_AMY", "uni_whiten_AMY ~ aromn + valmn +ActionGoal+order_final+ (valmn + ActionGoal|sub)","aromn","uni_whiten_AMY",  xlabel, ylabel, highcolor, "#424242", plotTitle, fnamepdf, fnamepng, 1)
```

##Relationship between amygdala activation and temporal memory
```{r}
tmpmod <- lmer(Tprecise_biasabs~uni_whiten_AMY + valmn + aromn +ActionGoal+order_final+ (valmn|sub), data=myDatabev_memfiltered, REML =FALSE)
summary(tmpmod)
anova(tmpmod)
```
```{r}
fnamepdf<-"YOURRESULTSDIR/Figures/RawPlots/uni_whiten_AMY_TempMem.pdf"
fnamepng<-"YOURRESULTSDIR/Figures/RawPlots/uni_whiten_AMY_TempMem.png"
# "#2859BB"
# '#1627BB'

xlabel<-"Amygdala Activation"
ylabel<-"Temporal Memory Error (abs)"
plotTitle <- ""


myGroupCorrelation_group_sub(myDatabev_memfiltered, "uni_whiten_AMY", "Tprecise_biasabs~uni_whiten_AMY + valmn +ActionGoal+order_final+ (valmn|sub)","uni_whiten_AMY","Tprecise_biasabs",  xlabel, ylabel, highcolor, "#EAA48F", plotTitle, fnamepdf, fnamepng, 1)
```
```{r}
tmpmod <- lmer(Tprecise_biasabs~uni_whiten_AMY + ReconMem + valmn + aromn +ActionGoal+order_final+ (valmn|sub), data=myDatabev_memfiltered, REML =FALSE)
summary(tmpmod)
anova(tmpmod)
```
##Relationship between perirhinal activation and emotion
```{r}
tmpmod <- lmer(uni_whiten_PRC ~ valmn + aromn +ActionGoal+order_final+ (valmn+ActionGoal|sub), data=myDatabev, REML =FALSE)
summary(tmpmod)
anova(tmpmod)
```

```{r}
fnamepdf<-"YOURRESULTSDIR/Figures/RawPlots/Corr_uniPRCwhiten_valmn.pdf"
fnamepng<-"YOURRESULTSDIR/Figures/RawPlots/Corr_uniPRCwhiten_valmn.png"
# "#2859BB"
# '#1627BB'

xlabel<-"Normative Valence Rating"
ylabel<-"Perirhinal Activity"
plotTitle <- ""

myGroupCorrelation_group_nosub(myDatabev, "uni_whiten_AMY", "uni_whiten_AMY ~ valmn + aromn +ActionGoal+order_final+ (valmn+ActionGoal|sub)", "valmn", "uni_whiten_AMY",  xlabel, ylabel, highcolor, "#54D388", plotTitle, fnamepdf, fnamepng, 1.4)
```

##Relationship between perirhinal and amygdala activation
```{r}
tmpmod <- lmer(uni_whiten_PRC ~ uni_whiten_AMY+ valmn + aromn +ActionGoal+order_final+ (valmn + ActionGoal|sub), data=myDatabev, REML =FALSE)
summary(tmpmod)
anova(tmpmod)
```
```{r}
fnamepdf<-"YOURRESULTSDIR/Figures/RawPlots/Corr_uniPRC_uniAMYwhiten.pdf"
fnamepng<-"YOURRESULTSDIR/Figures/RawPlots/Corr_uniPRC_uniAMYwhiten.png"
# "#2859BB"
# '#1627BB'

xlabel<-"Amygdala Activity"
ylabel<-"Perirhinal Activity"
plotTitle <- ""

myGroupCorrelation_group_sub(myDatabev, "uni_whiten_PRC", "uni_whiten_PRC ~ uni_whiten_AMY+ valmn + aromn +ActionGoal+order_final+ (valmn|sub)", "uni_whiten_AMY", "uni_whiten_PRC",  xlabel, ylabel, highcolor, "#54D388", plotTitle, fnamepdf, fnamepng, 1)
```


##Relationship between perirhinal activation and item memory

```{r}
tmpmod <- lmer(uni_whiten_PRC~ ReconMem*ConfReconMem + valmn + aromn + ActionGoal+order_final+ (ActionGoal + valmn|sub), data=myDatabev_memfiltered,REML =FALSE)
summary(tmpmod)
anova(tmpmod)
```
test coeffient significance
```{r}
trends <- lstrends(tmpmod, pairwise ~ ReconMem, var = "ConfReconMem", pbkrtest.limit = 12552)
summary(trends)
```
```{r}
# Extract estimated trends
trends_estimates <- trends$lstrends

# Test if the slopes are significantly different from 0
tests <- test(trends_estimates)
tests
# Summarize the tests to get p-values
summary(tests)
```

```{r}
#plot interaction
fname = "YOURRESULTSDIR/Figures/RawPlots/uniwhitePRCvsItemMemConfinter.pdf"
ylabel = "Perirhinal Activation"
#Plot it
p <- interact_plot(tmpmod, pred=ConfReconMem, modx = ReconMem,  x.label = "Item Memory Confidence", legend.main = "Item Memory", y.label = ylabel, interval = TRUE,  line.thickness = 1, int.type = "confidence", colors = c("#6D6E71", "#BCBEC0"))+ theme_classic(20)+
  
  theme(axis.title.y = element_text(size = rel(1), angle = 90,  vjust=1.25))+
  theme(axis.title.x = element_text(size = rel(1), angle = 0,  vjust=0))+
  theme(axis.text.x = element_text(size=rel(1)))+
  theme(axis.text.y = element_text(size=rel(1)))+
  theme(axis.line = element_line(colour = 'black', size = 0.5))+
  theme(axis.ticks = element_line(colour = "black", size = 0.5))+
      theme(axis.title.y = element_text(size = rel(0.85), angle = 90,  vjust=1.25))+
  theme(axis.title.x = element_text(size = rel(0.85), angle = 0,  vjust=0))+
  theme(axis.text.x = element_text(size=rel(0.85)))+
  theme(axis.text.y = element_text(size=rel(0.85)))+
  scale_y_continuous(labels = scales::number_format(accuracy = 0.1,))+
  labs(title = "")

ggsave(fname,height=4, width=6.5, dpi=300, device=cairo_pdf)
```


Plot remembered only with dot plots
```{r}
reconOnly <- myDatabev_memfiltered[myDatabev_memfiltered$ReconMem == "Remembered",]
library(dplyr)
groupdf<-reconOnly %>% group_by(sub, ConfReconMem)%>%dplyr::summarize(uni_whiten_PRC = mean(uni_whiten_PRC, na.rm=TRUE))
detach("package:dplyr", force=TRUE)
sumdf <- summarySEwithin(groupdf, measurevar="uni_whiten_PRC", idvar="sub",withinvars=c("ConfReconMem"), na.rm=TRUE, conf.interval=.95)
xlab = "Item Memory Confidence"
ylab = "Perirhinal Activation"
ymin = min(sumdf$uni_whiten_PRC) - 1*max(sumdf$se)
ymax =  max(sumdf$uni_whiten_PRC) + 1*max(sumdf$se)
fnpdf = "YOURRESULTSDIR/Figures/RawPlots/PRCvsItemMemConfDotPlot.pdf"
fnpng = "YOURRESULTSDIR/Figures/RawPlots/PRCvsItemMemConfDotPlot.png"

dotPlotOnefactor(sumdf, "ConfReconMem", "uni_whiten_PRC", xlab, ylab,  ymin, ymax, fnpdf, fnpng, "#1F1F1F", 4, 3.4, 0.1)
##54D388
```


##Relationship between perirhinal activation and temporal memory 
```{r}
tmpmod <- lmer(Tprecise_biasabs~uni_whiten_PRC + valmn + aromn + ActionGoal+order_final+ (ActionGoal + valmn|sub), data=myDatabev_memfiltered, REML =FALSE)
summary(tmpmod)
anova(tmpmod)
```

```{r}
fnamepdf<-"YOURRESULTSDIR/Figures/RawPlots/uni_whiten_PRC_TempMem.pdf"
fnamepng<-"YOURRESULTSDIR/Figures/RawPlots/uni_whiten_PRC_TempMem.png"
# "#2859BB"
# '#1627BB'

xlabel<-"Perirhinal Activition"
ylabel<-"Temporal Memory Error (abs)"
plotTitle <- ""


myGroupCorrelation_group_sub(myDatabev_memfiltered, "uni_whiten_PRC", "Tprecise_biasabs~uni_whiten_PRC + valmn +ActionGoal+order_final+ (valmn|sub)","uni_whiten_PRC", "Tprecise_biasabs", xlabel, ylabel, highcolor, "#54D388", plotTitle, fnamepdf, fnamepng, 1)
```
```{r}
tmpmod <- lmer(Tprecise_biasabs~uni_whiten_PRC + ReconMem + valmn + aromn +ActionGoal+order_final+ (ActionGoal+valmn|sub), data=myDatabev_memfiltered, REML =FALSE)
summary(tmpmod)
anova(tmpmod)
```


###Interaction model: perirhinal activation and sesion time
```{r}
    tmpmod <- lmer(Tprecise_biasabs~uni_whiten_PRC*TrealCat+valmn+aromn+ActionGoal+order_final+ (ActionGoal+valmn|sub), data=myDatabev_memfiltered, REML =FALSE, control = lmerControl(optimizer = "bobyqa"))
    summary(tmpmod)
    anova(tmpmod)
```

```{r}
    tmpmod <- lmer(Tprecise_biasabs~uni_whiten_PRC*TrealCat+ReconMem + valmn+aromn+ActionGoal+order_final+ (ActionGoal+valmn|sub), data=myDatabev_memfiltered, REML =FALSE, control = lmerControl(optimizer = "bobyqa"))
    summary(tmpmod)
    anova(tmpmod)
```
test coeffient significance
```{r}
trends <- lstrends(tmpmod, pairwise ~ TrealCat, var = "uni_whiten_PRC", pbkrtest.limit = 12552)
summary(trends)
```
```{r}
# Extract estimated trends
trends_estimates <- trends$lstrends

# Test if the slopes are significantly different from 0
tests <- test(trends_estimates)
tests
# Summarize the tests to get p-values
summary(tests)
```
```{r}
#plot interaction
fname = "YOURRESULTSDIR/Figures/RawPlots/Interaction_RealTimePRCwhiten_TempBiasAbsCat.pdf"
ylabel = "Temporal Memory Error (abs)"
#Plot it
p <- interact_plot(tmpmod, pred=uni_whiten_PRC, modx = TrealCat,
              modx.values = c("Early","Mid","Late"),  legend = "Session Time", x.label = "Perirhinal Activation", y.label = ylabel, interval = TRUE,  line.thickness = 1,linetypes = rep("solid", 3), int.type = "confidence", colors = c("#C8E5CC", "#9FCDB1", "#12AD4B"))+ theme_classic(20)+
scale_linetype_manual(values = c("solid", "solid", "solid"))+
  
  theme(axis.title.y = element_text(size = rel(1), angle = 90,  vjust=1.25))+
  theme(axis.title.x = element_text(size = rel(1), angle = 0,  vjust=0))+
  theme(axis.text.x = element_text(size=rel(1)))+
  theme(axis.text.y = element_text(size=rel(1)))+
  theme(axis.line = element_line(colour = 'black', size = 0.5))+
  theme(axis.ticks = element_line(colour = "black", size = 0.5))+
      theme(axis.title.y = element_text(size = rel(0.85), angle = 90,  vjust=1.25))+
  theme(axis.title.x = element_text(size = rel(0.85), angle = 0,  vjust=0))+
  theme(axis.text.x = element_text(size=rel(0.85)))+
  theme(axis.text.y = element_text(size=rel(0.85)))+
  scale_y_continuous(labels = scales::number_format(accuracy = 0.1,))+
  labs(title = "")

ggsave(fname,height=4, width=6, dpi=300, device=cairo_pdf)
```


```{r}
    tmpmod <- lmer(Tprecise_bias~uni_whiten_PRC*TrealCat+ ReconMem +valmn+aromn+ActionGoal+order_final+ (valmn|sub), data=myDatabev_memfiltered, REML =FALSE, control = lmerControl(optimizer = "bobyqa"))
    summary(tmpmod)
    anova(tmpmod)
```

```{r}
    tmpmod <- lmer(Tprecise_bias~uni_whiten_PRC*TrealCat+valmn+aromn+ActionGoal+order_final+ (valmn|sub), data=myDatabev_memfiltered, REML =FALSE, control = lmerControl(optimizer = "bobyqa"))
    summary(tmpmod)
    anova(tmpmod)
```
test coeffient significance
```{r}
trends <- lstrends(tmpmod, pairwise ~ TrealCat, var = "uni_whiten_PRC", pbkrtest.limit = 12552)
summary(trends)
```
```{r}
# Extract estimated trends
trends_estimates <- trends$lstrends

# Test if the slopes are significantly different from 0
tests <- test(trends_estimates)
tests
# Summarize the tests to get p-values
summary(tests)
```
```{r}
#plot interaction
fname = "YOURRESULTSDIR/Figures/RawPlots/Interaction_RealTimePRCwhiten_TempBiasCat.pdf"
ylabel = "Temporal Memory Error"
#Plot it
p <- interact_plot(tmpmod, pred=uni_whiten_PRC, modx = TrealCat,
              modx.values = c("Early","Mid","Late"),  legend = "Session Time", x.label = "Perirhinal Activation", y.label = ylabel, interval = TRUE,  line.thickness = 1,linetypes = rep("solid", 3), int.type = "confidence", colors = c("#C8E5CC", "#9FCDB1", "#12AD4B"))+ theme_classic(20)+
scale_linetype_manual(values = c("solid", "solid", "solid"))+
  
  theme(axis.title.y = element_text(size = rel(1), angle = 90,  vjust=1.25))+
  theme(axis.title.x = element_text(size = rel(1), angle = 0,  vjust=0))+
  theme(axis.text.x = element_text(size=rel(1)))+
  theme(axis.text.y = element_text(size=rel(1)))+
  theme(axis.line = element_line(colour = 'black', size = 0.5))+
  theme(axis.ticks = element_line(colour = "black", size = 0.5))+
      theme(axis.title.y = element_text(size = rel(0.85), angle = 90,  vjust=1.25))+
  theme(axis.title.x = element_text(size = rel(0.85), angle = 0,  vjust=0))+
  theme(axis.text.x = element_text(size=rel(0.85)))+
  theme(axis.text.y = element_text(size=rel(0.85)))+
  labs(title = "")

ggsave(fname,height=4, width=6, dpi=300, device=cairo_pdf)
```


#Relationship between within-trial pattern correlation and temporal memory accuracy
**Plot the TR by TR autocorrelation by mask**
```{r}
masks<-c("harvardoxford_Hippocampus_bin60_2mm", "FS_FPl")
for (ThisMask in masks){
  myData_subset= subset(myDataAll_memfiltered, mask==ThisMask)
  ylabel=sprintf("%s Autocorrelation (z)", transform_string(ThisMask))
  fnamepdf=sprintf("YOURRESULTSDIR/Figures/RawPlots/%s_TRpairs_autocorrelation.pdf", ThisMask)
  fnamepng=sprintf("YOURRESULTSDIR/Figures/RawPlots/%s_TRpairs_autocorrelation.png", ThisMask)
  #neg vs pos
  tmp_subset <- myData_subset[myData_subset$TRpairs %in% c("0_1", "1_2", "2_3", "3_4") & myData_subset$PerciseBiasFlag %in% c("MemSuccess", "MemFail"),]
  
  if (ThisMask == "harvardoxford_Hippocampus_bin60_2mm"){
  colorvalue = c("#BDDDEE", "#077EAD")
}
else if (ThisMask == "FS_FPl"){
  colorvalue = c("#D6BFD1", "#AD4993")
}
else{colorvalue = c("#BEBEBE", "#424242")}
  
  #calculate summary 
  library(dplyr)
  tmp_subset<-tmp_subset %>% group_by(sub, PerciseBiasFlag, TRpairs)%>%dplyr::summarize(corr_z=mean(corr_z, na.rm=TRUE))
  detach("package:dplyr", force=TRUE)
  tmp_negpos_sum <- summarySEwithin(tmp_subset, measurevar="corr_z",  idvar=c("sub"),withinvars=c("PerciseBiasFlag", "TRpairs"), na.rm=TRUE, conf.interval=.95)
  library(dplyr)
  ymax <- max(tmp_negpos_sum$corr_z) + max(tmp_negpos_sum$se)
  #plot lines and save
  # Line plot with multiple groups
ggplot(data=tmp_negpos_sum, aes(x=TRpairs, y=corr_z, group=PerciseBiasFlag)) +
  geom_errorbar(aes(ymin=corr_z-se, ymax=corr_z+se), width=.1) +
  geom_line(aes(color=PerciseBiasFlag), size = 0.4)+
  geom_point(aes(color=PerciseBiasFlag), size = 0.4)+
  ylab(ylabel)+
  xlab("TR pairs")+
  theme(legend.position = "right")+
  # annotate(
  #     "text", x = Inf, y = ymax+0.005, label = text_label, 
  #     hjust = 1, vjust = 1, size = 3, color = "black") +
  scale_color_manual(values=colorvalue, name = "Temporal Memory",labels = c("Low", "High"))+
theme_classic(base_size = 20) +
  theme(axis.title.y = element_text(size = rel(1), angle = 90,  vjust=1.25))+
  theme(axis.title.x = element_text(size = rel(1), angle = 0,  vjust=0))+
  theme(axis.text.x = element_text(size=rel(1)))+
  theme(axis.text.y = element_text(size=rel(1)))+
  # theme(legend.position="none")+
  theme(axis.line = element_line(colour = 'black', size = 0.5))+
  theme(axis.ticks = element_line(colour = "black", size = 0.5))+
      theme(axis.title.y = element_text(size = rel(0.85), angle = 90,  vjust=1.25))+
  theme(axis.title.x = element_text(size = rel(0.85), angle = 0,  vjust=0))+
  theme(axis.text.x = element_text(size=rel(0.85)))+
  theme(axis.text.y = element_text(size=rel(0.85)))+
  scale_y_continuous(labels = scales::number_format(accuracy = 0.01,))+
  labs(title = "")
        # panel.grid.major = element_blank(),
        # panel.grid.minor = element_blank())
 ggsave(fnamepdf,height=4, width=7, dpi=300)
  ggsave(fnamepng,height=4, width=7, dpi=300)
  
}
```
FPl
```{r}
myData_subset= subset(myDataAll_memfiltered, mask=="FS_FPl")
  tmp_subset <- myData_subset[myData_subset$TRpairs %in% c("0_1", "1_2", "2_3", "3_4") & myData_subset$PerciseBiasFlag %in% c("MemSuccess", "MemFail"),]
  mod <- lmer(corr_z~PerciseBiasFlag*TRpairs + valmn + aromn + ActionGoal + order + lum_rgb + (valmn + ActionGoal|sub), control = lmerControl(optimizer = "bobyqa"), data=tmp_subset, REML =FALSE)
  summary(mod)
  anova(mod)
  emmeans(mod, pairwise ~ PerciseBiasFlag*TRpairs, adjust = "none")
```

##Relationship between within-trial pattern correlation and temporal memory accuracy (linear) 
```{r}
corrBeta <- c()
corrp <- c()

valmnbeta <- c()
valmnp <- c()

aromnbeta <- c()
aromnp <- c()

ActionGoalbeta <- c()
ActionGoalp <- c()

Maskli <- c()
TRpairli <- c()

maskli <- c("FS_FPl", "harvardoxford_Hippocampus_bin60_2mm")
for (tmpMask in maskli){
# for (tmpMask in unique(myDataAll_memfiltered$mask)){
  for (TRnow in c("3_4")){
    #test
    #tmpMask <- "FS_FPl"
    #TRnow <- "3_4"
    tmpdf <- myDataAll_memfiltered[myDataAll_memfiltered$mask==tmpMask & myDataAll_memfiltered$TRpairs==TRnow,]
    
    tmpmod <- lmer(Tprecise_biasabs~corr_z + valmn + aromn + ActionGoal+order_final+ lum_rgb+ (ActionGoal + valmn|sub), data=tmpdf, REML =FALSE, control = lmerControl(optimizer = "bobyqa"))
    summod <- summary(tmpmod)
    aovmod <- anova(tmpmod)
    
    corrBeta <- append(corrBeta, round(summod[["coefficients"]][2, 1], 3))
    corrp <- append(corrp, round(aovmod$`Pr(>F)`[1], 3))
    
    valmnbeta <- append(valmnbeta, round(summod[["coefficients"]][3, 1], 3))
    valmnp <- append(valmnp, round(aovmod$`Pr(>F)`[2], 3))
    
    aromnbeta <- append(aromnbeta, round(summod[["coefficients"]][4, 1], 3))
    aromnp <- append(aromnp, round(aovmod$`Pr(>F)`[3], 3))
  
    ActionGoalbeta <- append(ActionGoalbeta, round(summod[["coefficients"]][5, 1], 3))
    ActionGoalp <- append(ActionGoalp, round(aovmod$`Pr(>F)`[4], 3))
  
    # InterValCorrbeta <- append(InterValCorrbeta, round(summod[["coefficients"]][12, 1], 3))
    # InterValCorrp <- append(InterValCorrp, round(aovmod$`Pr(>F)`[5], 3))
    
    Maskli <- append(Maskli, tmpMask)
    TRpairli <- append(TRpairli, TRnow)

    fnamepdf<-sprintf("YOURRESULTSDIR/Figures/RawPlots/Corrbiasabs_%s_%s.pdf",  tmpMask, TRnow)
fnamepng<-sprintf("YOURRESULTSDIR/Figures/RawPlots/Corrbiasabs_%s_%s.png",  tmpMask, TRnow)
# "#2859BB"
# '#1627BB'

xlabel<-sprintf("%s Autocorrelation (z)", transform_string(tmpMask))
ylabel<-"Temporal Memory Error (abs)"
plotTitle <- ""

if (tmpMask=="FS_FPl"){
  regressline <- "#B64097"
}
else{
  regressline <- "#95BBD8"
}

myGroupCorrelation_group_sub(tmpdf, "corr_z", "Tprecise_biasabs~corr_z + valmn + ActionGoal+order_final+ lum_rgb+ (valmn+ActionGoal|sub)","corr_z","Tprecise_biasabs",  xlabel, ylabel, highcolor, regressline, plotTitle, fnamepdf, fnamepng, 1)
  }
}
sumCorrBias_corr_memfilter <- data.frame(Maskli, TRpairli, corrBeta, corrp, valmnbeta, valmnp, ActionGoalbeta, ActionGoalp)
```

### HPC
```{r}
tmpMask <- "harvardoxford_Hippocampus_bin60_2mm"
TRnow <- "3_4"
tmpdf <- myDataAll_memfiltered[myDataAll_memfiltered$mask==tmpMask & myDataAll_memfiltered$TRpairs==TRnow,]
    
    tmpmod <- lmer(Tprecise_biasabs~corr_z + valmn+aromn + ActionGoal+order_final+ lum_rgb+ (valmn+ActionGoal|sub), data=tmpdf, REML =FALSE, control = lmerControl(optimizer = "bobyqa"))
    summary(tmpmod)
    anova(tmpmod)
```


```{r}
tmpMask <- "harvardoxford_Hippocampus_bin60_2mm"
TRnow <- "3_4"
tmpdf <- myDataAll_memfiltered[myDataAll_memfiltered$mask==tmpMask & myDataAll_memfiltered$TRpairs==TRnow,]
    
    tmpmod <- lmer(Tprecise_biasabs~corr_z + ReconMem + valmn+aromn + ActionGoal+order_final+ lum_rgb+ (valmn+ActionGoal|sub), data=tmpdf, REML =FALSE, control = lmerControl(optimizer = "bobyqa"))
    summary(tmpmod)
    anova(tmpmod)
```

###FPl
```{r}
tmpMask <- "FS_FPl"
TRnow <- "3_4"
tmpdf <- myDataAll_memfiltered[myDataAll_memfiltered$mask==tmpMask & myDataAll_memfiltered$TRpairs==TRnow,]
    
    tmpmod <- lmer(Tprecise_biasabs~corr_z + valmn+aromn + ActionGoal+order_final+ lum_rgb+ (valmn+ActionGoal|sub), data=tmpdf, REML =FALSE, control = lmerControl(optimizer = "bobyqa"))
    summary(tmpmod)
    anova(tmpmod)
```

```{r}
tmpMask <- "FS_FPl"
TRnow <- "3_4"
tmpdf <- myDataAll_memfiltered[myDataAll_memfiltered$mask==tmpMask & myDataAll_memfiltered$TRpairs==TRnow,]
    
    tmpmod <- lmer(Tprecise_biasabs~corr_z +ReconMem + valmn+aromn + ActionGoal+order_final+ lum_rgb+ (valmn+ActionGoal|sub), data=tmpdf, REML =FALSE, control = lmerControl(optimizer = "bobyqa"))
    summary(tmpmod)
    anova(tmpmod)
```









































