---
title: "Mediations"
author: "Jingyi"
date: "2025-06-11"
output: pdf_document
---

###brms
```{r}
rm(list=ls(all=TRUE)) 
```

```{r}
library(pacman)
p_load("brms", "posterior", "bayestestR", "dplyr", "tidyverse")
```


```{r}
summarize_path <- function(x) {
  data.frame(
    mean = mean(x),
    ci_lower = quantile(x, 0.025),
    ci_upper = quantile(x, 0.975),
    p_val = 1-mean(x > 0),  
    p_val_neg = 1-mean(x < 0) 
  )
}
```


```{r}
tmpMask <- "FS_FPl"
TRnow <- "3_4"
tmpdf <- myDataAll_memfiltered[myDataAll_memfiltered$mask==tmpMask & myDataAll_memfiltered$TRpairs==TRnow,]
```
zscore across subjects
```{r}
tmpdf <- tmpdf %>% dplyr::mutate(
    Tprecise_biasabs_z = as.numeric(scale(Tprecise_biasabs)),
    Tprecise_bias_z = as.numeric(scale(Tprecise_bias)))
```

##pathway 1: Valmn -> uni_AMY -> FPl (within-trial pattern correlation) -> TM
```{r}
model_serial1 <- brm(
  # Step 1: uni_AMY ~ valmn
  bf(uni_whiten_AMY ~ valmn + aromn  + ActionGoal + order_final + (valmn + ActionGoal || sub)) +
  
  # Step 2: corr_z ~ uni_AMY
  bf(corr_z ~ uni_whiten_AMY + aromn + ActionGoal + order_final + lum_rgb + (ActionGoal || sub)) +
  
  # Step 3: Tprecise_biasabs ~ corr_z
  bf(Tprecise_biasabs_z ~ corr_z + valmn + aromn + ActionGoal + order_final + lum_rgb + (valmn + ActionGoal || sub)) +
  
  set_rescor(FALSE),
  data = tmpdf,
  prior = set_prior("normal(0, 2.5)", class = 'b'),
  chains = 4,
  cores = 4,
  iter = 4000,
  control = list(max_treedepth = 15, adapt_delta = 0.95),
  seed = 123
)
```

```{r}
# the direct effects
results <- as.data.frame(describe_posterior(model_serial1, ci_method = "HDI", centrality = "mean", test = "pd")) %>% print
```

**Get beta**
get posterior
```{r}
post <- posterior_samples(model_serial1)
post$p1 <- post$b_uniwhitenAMY_valmn
post$p2 <- post$b_corrz_uni_whiten_AMY
post$p3 <- post$b_Tprecisebiasabsz_corr_z
post$indirect_serial <- post$b_uniwhitenAMY_valmn * post$b_corrz_uni_whiten_AMY * post$b_Tprecisebiasabsz_corr_z
post$direct_effect <- post$b_Tprecisebiasabsz_valmn
post$total_effect <- post$indirect_serial + post$direct_effect

post$prop_mediated <- post$indirect_serial / post$total_effect

results <- as.data.frame(describe_posterior(post[, c("p1", "p2", "p3", "indirect_serial", "direct_effect", "total_effect", "prop_mediated")], ci_method = "HDI", centrality = "mean", test = "pd", round = 6))
View(results)
```
```{r}
post %>%
  ggplot(aes(x = indirect_serial, fill = factor(0), color = factor(0))) +
  geom_density(alpha = .5) +
  # scale_color_ptol() +
  # scale_fill_ptol() +
  scale_y_continuous(NULL, breaks = NULL) +
  labs(title = "The serial indirect effect of valence on temporal memory via AMY-FPl pathway", x = NULL) +
  theme_minimal() +
  theme(legend.position = "none")
```

Get p
```{r}
beta_results <- list(
  p1 = summarize_path(post$b_uniwhitenAMY_valmn),
  p2 = summarize_path(post$b_corrz_uni_whiten_AMY),
  p3 = summarize_path(post$b_Tprecisebiasabsz_corr_z),
  indirect = summarize_path(post$b_uniwhitenAMY_valmn * post$b_corrz_uni_whiten_AMY * post$b_Tprecisebiasabsz_corr_z),
  direct = summarize_path(post$b_Tprecisebiasabsz_valmn),
  total = summarize_path(post$indirect_serial + post$direct_effect),
  prop_mediated = summarize_path(post$indirect_serial / post$total_effect)
)

do.call(rbind, beta_results)
```

Get prior
```{r}
get_prior(model_serial1$formula, data = tmpdf, family = gaussian())
# or after fitting:
prior_summary(model_serial1)
```

##pathway 2 modulated mediation (directional) via perirhinal cortex
valmn -> uni_PRC -> ConfReconMem*Trealcat -> TM
```{r}
#get remember only
tmpdf_rem <- tmpdf[tmpdf$ReconMem == "Recognized",]
#relevel "late" to be the reference
tmpdf_rem$TrealCat <- relevel(tmpdf_rem$TrealCat, ref = "Late")
levels(tmpdf_rem$TrealCat)

#model for the mediator (valmn->ConfReconMem)
fit_M1_PRCmod6 <- brm(
  formula = uni_whiten_PRC ~ valmn + aromn + ActionGoal+order_final+ (valmn||sub), 
  # set_rescor(FALSE),
  data = tmpdf_rem,
  family = gaussian(),
  prior = set_prior("normal(0, 2.5)", class = 'b'),
  chains = 4,
  cores = 4,
  iter = 4000,
  control = list(max_treedepth = 15, adapt_delta = 0.95),
  seed = 123
)

#model for the mediator (ConfReconMem -> uni_PRC)
fit_M2_PRCmod6 <- brm(
  formula = ConfReconMem ~ uni_whiten_PRC + valmn + aromn + ActionGoal+order_final+ (valmn||sub), 
  # set_rescor(FALSE),
  data = tmpdf_rem,
  family = gaussian(),
  prior = set_prior("normal(0, 2.5)", class = 'b'),
  chains = 4,
  cores = 4,
  iter = 4000,
  control = list(max_treedepth = 15, adapt_delta = 0.95),
  seed = 123
)

#model for outcome (TM) with moderation
fit_Y_PRCmod6 <- brm(
  formula = Tprecise_bias_z~uni_whiten_PRC+ConfReconMem*TrealCat+valmn+aromn+ActionGoal+order_final+ (valmn||sub),
  # set_rescor(FALSE),
  prior = set_prior("normal(0, 2.5)", class = 'b'),
  data = tmpdf_rem,
  family = gaussian(),
  chains = 4,
  cores = 4,
  iter = 4000,
  control = list(max_treedepth = 15, adapt_delta = 0.95),
  seed = 123
)
```
get posterior
```{r}
post_M1 <- as_draws_df(fit_M1_PRCmod6)
post_M2 <- as_draws_df(fit_M2_PRCmod6)
post_Y <- as_draws_df(fit_Y_PRCmod6)

#a_path: valmn->ConfReconMem
post$a1 <- post_M1$b_valmn
#a2_path: ConfReconMem->PRC
post$a2 <- post_M2$b_uni_whiten_PRC
#b1_path: PRC main effect on TempMem
post$b1 <- post_Y$b_ConfReconMem
#b2_path moderation
post$b3_2 <- post_Y$`b_ConfReconMem:TrealCatEarly`
post$b3_3 <- post_Y$`b_ConfReconMem:TrealCatMid`

#indirect effects
post$ind1 <- (post$a1)*(post$a2)*(post$b1)
post$ind2 <- (post$a1)*(post$a2)*(post$b1 + post$b3_2)
post$ind3 <- (post$a1)*(post$a2)*(post$b1 + post$b3_3)

#direct effect
post$direct_effect <- post_Y$b_valmn

# post$total_effect <- post$ind1 + post$direct_effect
# 
# post$prop_mediated <- post$indirect_serial / post$total_effect

results <- as.data.frame(describe_posterior(post[, c("a1","a2", "b1", "b3_2", "b3_3", "ind1", "ind2", "ind3", "direct_effect")], ci_method = "HDI", centrality = "mean", test = "pd", round = 6))
```

Get p
```{r}
beta_results <- list(
  a1 = summarize_path(post_M1$b_valmn),
  a2 = summarize_path(post_M2$b_uni_whiten_PRC),
  b1 = summarize_path(post_Y$b_ConfReconMem),
  b3_2 = summarize_path(post_Y$`b_ConfReconMem:TrealCatEarly`),
  b3_3 = summarize_path(post_Y$`b_ConfReconMem:TrealCatMid`),
  indirect1 = summarize_path((post_M1$b_valmn)*(post_M2$b_uni_whiten_PRC) * (post_Y$b_ConfReconMem)),
  indirect2 = summarize_path((post_M1$b_valmn)*(post_M2$b_uni_whiten_PRC) * (post_Y$b_ConfReconMem + post_Y$`b_ConfReconMem:TrealCatEarly`)),
  indirect3 = summarize_path((post_M1$b_valmn)*(post_M2$b_uni_whiten_PRC) * (post_Y$b_ConfReconMem + post_Y$`b_ConfReconMem:TrealCatMid`)),
  direct = summarize_path(post_Y$b_valmn)
)

do.call(rbind, beta_results)
```

##Pathway 3 (HPC between-trial pattern correlation)
```{r}
library(dplyr)
#load HPC neural similarity
HPC <- read.csv("YOURRESULTSDIR/RSA/RSAbymaskDemean/harvardoxford_Hippocampus_bin60_2mm_all_rsas_betas_whitened_trialwise_extended.csv")
HPC_select <- HPC %>%
  dplyr::select(
    sub, mask, run, corr_z, trial1, trial2, triallag,
    StimVal1, order, ImgStim1, Tprecise_biasabs1
  )
colnames(HPC_select) <- c("sub", "maskHPC", "run", "corr_z_HPC", "trial", "trial2", "triallag", "StimVal1",  "order", "ImgStim", "Tprecise_biasabs")
HPC_select <- HPC_select[HPC_select$triallag == 1,]

#Merge
tmpdfall <- dplyr::left_join(tmpdf, HPC_select, by = c("sub", "run", "trial", "Tprecise_biasabs", "ImgStim"))
```

```{r}
model_serial3 <- brm(
  # Step 1: uni_AMY ~ valmn
  bf(uni_whiten_AMY ~ valmn + aromn + ActionGoal + order_final + (valmn + ActionGoal || sub)) +
  
  # Step 2: corr_z ~ uni_AMY 
  bf(corr_z_HPC ~ uni_whiten_AMY  + aromn + ActionGoal + order_final + (ActionGoal || sub)) +
  
  # Step 3: Tprecise_biasabs ~ corr_z + uni_AMY + valmn
  bf(Tprecise_biasabs_z ~ corr_z_HPC + valmn + aromn + ActionGoal + order_final + (valmn + ActionGoal || sub)) +
  
  set_rescor(FALSE),
  prior = set_prior("normal(0, 2.5)", class = 'b'),
  data = tmpdfall,
  chains = 4,
  cores = 4,
  iter = 4000,
  control = list(max_treedepth = 15, adapt_delta = 0.95),
  seed = 123
)
```
get posterior
```{r}
post <- posterior_samples(model_serial3)
post$p1 <- post$b_uniwhitenAMY_valmn
post$p2 <- post$b_corrzHPC_uni_whiten_AMY
post$p3 <- post$b_Tprecisebiasabsz_corr_z_HPC
post$indirect_serial <- post$b_uniwhitenAMY_valmn * post$b_corrzHPC_uni_whiten_AMY * post$b_Tprecisebiasabsz_corr_z_HPC
post$direct_effect <- post$b_Tprecisebiasabsz_valmn
post$total_effect <- post$indirect_serial + post$direct_effect

post$prop_mediated <- post$indirect_serial / post$total_effect

results <- as.data.frame(describe_posterior(post[, c("p1", "p2", "p3", "indirect_serial", "direct_effect", "total_effect", "prop_mediated")], ci_method = "HDI", centrality = "mean", test = "pd", round = 6))
```

Get p
```{r}
beta_results <- list(
  p1 = summarize_path(post$b_uniwhitenAMY_valmn),
  p2 = summarize_path(post$b_corrzHPC_uni_whiten_AMY),
  p3 = summarize_path(post$b_Tprecisebiasabsz_corr_z_HPC),
  indirect = summarize_path(post$b_uniwhitenAMY_valmn * post$b_corrzHPC_uni_whiten_AMY * post$b_Tprecisebiasabsz_corr_z_HPC),
  direct = summarize_path(post$b_Tprecisebiasabsz_valmn),
  total = summarize_path(post$indirect_serial + post$direct_effect),
  prop_mediated = summarize_path(post$indirect_serial / post$total_effect)
)

do.call(rbind, beta_results)
```



##Test for paralell mediation
Valmn -> uni_AMY -> FPl -> TM
Valmn -> uni_AMY -> HPC -> TM
```{r}
model_parallel_3 <- brm(
  # M1: AMY ~ valmn
  bf(uni_whiten_AMY ~ valmn + aromn + ActionGoal + order_final+(valmn + ActionGoal || sub)) +
  
  # M2: corr_z ~ AMY 
  bf(corr_z ~ uni_whiten_AMY + aromn + ActionGoal + order_final +(ActionGoal || sub)) +
    
  # M2: corr_z ~ AMY 
  bf(corr_z_HPC ~ uni_whiten_AMY + aromn + ActionGoal + order_final +(ActionGoal || sub)) +
  
  
  # Final outcome: Tprecise_biasabs ~ corr_z + RPC + valmn
  bf(Tprecise_biasabs_z ~ corr_z + corr_z_HPC + valmn + aromn + ActionGoal + order_final + (valmn + ActionGoal || sub)) +
  
  set_rescor(FALSE),
  prior = set_prior("normal(0, 2.5)", class = 'b'),
  data = tmpdfall,
  chains = 4,
  cores = 4,
  iter = 4000,
  control = list(max_treedepth = 15, adapt_delta = 0.95),
  seed = 123
)
```
get posterior
```{r}
post <- posterior_samples(model_parallel_3)
post$p1 = post$b_uniwhitenAMY_valmn
  post$p2 = post$b_corrzHPC_uni_whiten_AMY
  post$p3 = post$b_corrz_uni_whiten_AMY
  post$p4 = post$b_Tprecisebiasabsz_corr_z_HPC
  post$p5 = post$b_Tprecisebiasabsz_corr_z
post$indirectHPC <- post$b_uniwhitenAMY_valmn*post$b_corrzHPC_uni_whiten_AMY*post$b_Tprecisebiasabsz_corr_z_HPC
post$indirectFPL <- post$b_uniwhitenAMY_valmn*post$b_corrz_uni_whiten_AMY*post$b_Tprecisebiasabsz_corr_z
post$direct_effect <- post$b_Tprecisebiasabsz_valmn
post$total_effect <- post$indirectHPC + post$indirectFPL + post$direct_effect
post$indirect_effect <- post$indirectHPC + post$indirectFPL

post$prop_mediated_1 <- post$indirectHPC + post$indirectFPL / post$total_effect
post$prop_mediated_2 <- post$indirectFPL/ post$total_effect

results <- as.data.frame(describe_posterior(post[, c("p1", "p2","p3","p4","p5","indirectHPC", "indirectFPL", "direct_effect", "total_effect", "prop_mediated_1", "prop_mediated_2")], ci_method = "HDI", centrality = "mean", test = "pd", round = 6))
```

Get p
```{r}
beta_results <- list(
  p1 = summarize_path(post$b_uniwhitenAMY_valmn),
  p2 = summarize_path(post$b_corrzHPC_uni_whiten_AMY),
  p3 = summarize_path(post$b_corrz_uni_whiten_AMY),
  p4 = summarize_path(post$b_Tprecisebiasabsz_corr_z_HPC),
  p5 = summarize_path(post$b_Tprecisebiasabsz_corr_z),
indirectHPC = summarize_path(post$b_uniwhitenAMY_valmn*post$b_corrzHPC_uni_whiten_AMY*post$b_Tprecisebiasabsz_corr_z_HPC),
indirectFPL = summarize_path(post$b_uniwhitenAMY_valmn*post$b_corrz_uni_whiten_AMY*post$b_Tprecisebiasabsz_corr_z),
direct_effect = summarize_path(post$b_Tprecisebiasabsz_valmn),
total_effect = summarize_path(post$indirectHPC + post$indirectFPL + post$direct_effect),
indirect_effect = summarize_path(post$indirectHPC + post$indirectFPL),

prop_mediated_1 = summarize_path(post$indirectHPC + post$indirectFPL / post$total_effect))

do.call(rbind, beta_results)
```


